---
title: "South Korea: The Case of A Long Democratization"
author: Ben
categories:
  - Korea
date: 12-11-2024
execute:
  warning: false
  message: false
  error: false
  echo: false    
---

# The Shock

The latest insurrection attempt by Yoon Seok-yeol of South Korea caught the world by surprise. It was widely believed that an affluent democracy with its cherished soft power would not be subject to a sudden political upheaval. \@\@\@ After all, South Korea is far above the structural 'thresholds' that political scientists have long reported, be it [ Argentine GDP in 1975](https://www.cambridge.org/core/books/democracy-and-development/4A5F43C449ADA81BDB9293D5B10D27C1) or [two decades of years](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1540-5907.2006.00201.x) beyond which a democratic regime might not fall.

Many have already offered extensive accounts on a litany of ways in which Yoon's martial law was unconstitutional and constitutes, in essence, an insurrection and perhaps a treason. One can easily find the whiff of anger, fury, or terror in them. There is one assumption common in these irrefutably rightful reactions--that South Korea was (nearing) to achieve the status of a consolidated democracy. A democracy that is so entrenched and irreversible that it is ["the only game in town"](https://www.press.jhu.edu/books/title/2194/problems-democratic-transition-and-consolidation?srsltid=AfmBOoqxsN9rgCP3-sEPfCeziUGht3xyaB2pj2QlAqFZ6o_shissSspp). Since the democratization in 1987, the hard-earned democratic institutions and organized citizens prevailed over a series of crises--no way it could be suddenly derailed!

Unless, of course, that assumption was invalid. What if, the post-1987 never amounted to a 'stable' democracy where any serious danger of collapse was reasonably negated? What if serious threats were always there? What if, when those threats occasionally manifested themselves, they were not taken as threats and understood as something else? What if South Korea is still in the middle of democratization that started in 1987, possibly similar to many transitional democracies around the world?

# Insurrection and Impeachment

# Democratic Survival vs. Consolidation

[Svolik](https://www.cambridge.org/core/journals/american-political-science-review/article/authoritarian-reversals-and-democratic-consolidation/E3963766F74CC6CF2AEE2F5B883139F4) demonstrates that democratic consolidation and democratic survival are two different factors. Institutional factors (presidentialism and previous military dictatorship) make a transitional regime *susceptible* to reversal, but the immediate trigger is a recession. As in:

> "\[E\]conomic development affects consolidation, and therefore whether a democracy faces a risk of a reversal, but it does not help us explain when a reversal might occur in transitional democracies. ... \[T\]he eventual timing of reversals is associated only with economic recessions."

# Did the insurrection come out of nowhere? The Deep Roots of the Insurrection

```{r}
#| include: false

library(dplyr)
library(vdemdata) 
library(ggplot2)
library(ggrepel)

df <- vdemdata::vdem %>%
  select(contains("v2x_polyarchy"), country_name, year) %>%
  filter(country_name == "South Korea")


df %>% 
  filter(year>1960) %>%
  mutate(graphid = 
           case_when(year>1987 & year<1993 ~ "red",
                     year>1992 & year<1998 ~ "red",
                     year>1997 & year<2003 ~ "blue",
                     year>2002 & year<2008 ~ "blue",
                     year>2007 & year<2013 ~ "red",
                     year>2012 & year<2017 ~ "red",
                     year>2016 & year<2022 ~ "blue",
                     year>2021 ~ "red")
  )  ->   df2

```

```{r}


df2 %>%
  ggplot(aes(x=year,
             y=v2x_polyarchy,
             alpha=0.7)) +
  geom_bar(aes(fill=graphid),
           stat = 'identity') +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "red")) +
  theme(legend.position = 'none') +
  labs(y="Polyarchy",
       title="Electoral Democracy. The higher, the more democratic")


```

```{r}


df4 <- vdemdata::vparty %>%
  select(v2xpa_antiplural, v2paenname, country_name, year) %>%
  mutate(dems = case_when(country_name == "South Korea" &
                            v2paenname %in% c(
                              "Democratic Justice Party",
                              "Democratic Liberal Party / New Korea Party",
                              "Liberty Korea Party",
                              "New World Party -- The Grand National Party"
                            ) ~ "red",
                          country_name == "South Korea" & v2paenname %in% c(
                            "Democratic Party",
                            "Democratic Party / Minjoo Party of Korea",
                            "Millenium Democratic Party",
                            "National Congress for New Politics / Democratic Party",
                            "Our Party",
                            "Party for Peace and Democracy",
                            "[United] Democratic Party"
                          ) ~ "blue", 
                          TRUE ~ "others"
  )) %>%
  mutate(korea = case_when(
    dems == "blue" ~ 1,
    dems == "red" ~ 1,
    dems == "others" ~ 0
  ))  

df4 %>% filter(year>1980) %>%
  ggplot(aes(x=year, 
             y=v2xpa_antiplural, 
             color=dems)) +
  geom_point(data = df4 %>% filter(year>1980) %>%
               filter(korea==1), 
             aes(size=4, alpha=0.75)) +
  geom_point(data = df4 %>% filter(year>1980) %>% 
               filter(korea==0),
             aes(size=1, alpha=0.5, color="grey")) +
  geom_smooth(data=df4 %>% filter(year>1980 &
                                    korea==0),
              color='#365d0f', se=FALSE) +
  annotate(geom="text", x=2000, y= 0.42, color="#365d0f", 
           label="Global Mean") +
  geom_label_repel(aes(label = v2paenname,
                       alpha = 0.7),
                   box.padding=4,
                   size=4,
                   data = df4 %>% filter(year==2016 & korea==1)) +
  theme_minimal() +
  scale_color_manual(values = c("blue", "grey", "red")) +
  theme(legend.position = 'none') +
  labs(y="anti-pluralism",
       title = "Anti-Pluralism Party Index. The higher, the less democratic") +
  geom_vline(xintercept = 1987,
             linetype=2)

```

```{r}



df4 %>% 
  filter(year>1980 & country_name=="United Kingdom") %>%
  filter(v2paenname == "Conservatives" | v2paenname == "Labour") -> df5

df5 %>%
  ggplot(aes(x=year,
             y=v2xpa_antiplural,
             color=v2paenname,
             label=v2paenname,
             alpha=0.75)) +
  geom_point(size=5) +
  geom_label_repel(data=df5 %>% filter(year==2017),
                   box.padding = 3, size=4) +
  theme_minimal() +
  theme(legend.position = 'none') +
  labs(y="anti-pluralism",
       title = "Anti-Pluralism Party Index. The higher, the less democratic") +
  ylim(0, 1)

```
