---
title: "Syllabus: GLOA 610 Economic Globalization & Development"
subtitle: Fall 2025. <br> Hybrid. F2F lecture, 7:20--9 PM (T) + online <br> [Innovation Hall 330](https://maps.app.goo.gl/qKt8oZPFcbQzFc5u8)
format: 
  html:
#    math: mathjax
    number-sections: true
    theme: cosmo
    table-markdown: true
#editor: visual
# author:
#   - name: "Byunghwan 'Ben' Son (bson3@gmu.edu)"
#     meta-data:
#       custom-info: "Office Hours"
#     affiliations:
#       - name: Global Affairs, George Mason University
#         url: https://globalaffairs.gmu.edu/


#csl: C:\\Users\\kalka\\Dropbox\\latex\\apsa.csl
toc: true
toccolor: blue
smooth-scroll: true

execute:
  warning: false
  message: false
  error: false
  echo: false
bibliography: references.bib
---

```{=html}
<style>


mark {
  background-color: #ece985;
  color: black;
  border-radius: 5px; 
  padding: 0.2em;
}

mark2 {
  background-color: #840a73;
  color: white;
  border-radius: 5px; 
  padding: 0.2em;
}

red {
  color: #9b1212;
}

blue {
  color: #124921;
}

</style>
```

**Change log** 

- <font size=2>Sep. 2: A new (short) reading added to the week of immigration (Reuters)</font>
- <font size=2>Sep. 9: A short news article added to the week of finance</font>



# Instructor

-   Byunghwan 'Ben' Son (bson3\@gmu.edu)
    -   Associate Professor of Global Affairs
    -   [{{< fa house size=small >}} Personal Webpage](https://textvulture.github.io/)
    -   [{{< fa school-flag size=small >}} GLOA Profile](https://globalaffairs.gmu.edu/)
    -   [{{< fa brands github >}} Github](https://github.com/textvulture)
    -   [{{< fa brands google-scholar >}} Google Scholar](https://scholar.google.com/citations?user=h0o27GgAAAAJ&hl=en)
-   Office Hours
    -   Office Hours 1:30-3:00 PM, TR. 6235 [Horizon Hall](https://maps.app.goo.gl/4QEBDLp3j4YNuVLB9)
-   Email Communications
    -   You can email me whenever you want, but my responses to the emails sent to me after 5 pm weekdays as well as any time during the weekend will be significantly slow.
    -   For your own interest, you might want to try to use the normal working hours (9 AM to 5 PM, Monday through Friday). In your email, please indicate <red>who you are</red> and <red>which class you’re in (i.e., GLOA 610)</red>.
    -   For security reasons, emails not sent from the Mason account (i.e., gmu.edu) won't be answered. This is the University policy.

# Course Description

Does globalization treat everybody equally (every country, every society, every region, or every system)? Throughout the semester, we will be grappling with this simple question in several different contexts. Particularly, we will navigate various avenues of economic globalization including trade, finance, debt, and investment to discuss to what extent globalization affects the economic well-being of nation-states, societies, and people around the world. In doing so, we will often employ conflicting ideological/theoretical perspectives. Throughout, we will also consider the “what should be done” questions: If globalization brings about prosperity, how can we make it more equitable and effective? If globalization traps people in misery, what can ameliorate it? Note that there hardly is a ‘right’ answer—or any answer—to any of these questions. By the end of the semester, students are expected to be familiar with the current literature on (and issues in general about) economic globalization and able to critically evaluate them. 

Two additional things to note:

- This ain't <red>no</red> econ class. Nor am I an economist.
- This is a <red>hybrid</red> class. The face-to-face (7:30-9 PM, T) portion of the class is for lecture and in-class discussions. The asynchronous portion, implemented through our course page in Canvas, is for your presentations (see @sec-report for details).

# COURSE REQUIREMENT

In a nutshell, your grade is determined by:

-   Reading Summaries (5% $\times$ 4 = 20%) @sec-read
-   Participation (20%) @sec-part
-   Case Report including a video presentation (20 $\times$ 2 = 40%) @sec-report
-   Final Exam (20%) @sec-final

## Readings (Reading Summaries) {#sec-read}

-   Completing all the required readings is only a minimal requirement for a graduate seminar. We build on it. If you didn't complete the reading, coming to class is quite meaningless. Our class discussions will be firmly anchored to the readings. I mean, we're literally discussing each of the readings. So be prepared.

-   Sometimes it might feel like you simply didn't get the reading despite putting in quite a bit of effort. That's completely okay. What is not okay is not asking questions that you had while reading them and leaving your curiosity unaddressed. That's a capital crime.

-   The assigned readings are not 'textbooks' in a traditional sense. I don't necessarily endorse or agree with them (in fact, there are some readings whose arguments I squarely disagree with). And some--though only a few--of the readings can be a bit provocative, if not misleading. These readings are here to help us think about the topics. In other words, you ain't no undergrad anymore and should be able to critically (but also productively) evaluate the readings.

-   Students are expected to about *some*--though maybe not all--of the following questions while working on the required readings.

-   What are the central arguments of the piece and the rationale behind them?

-   How can this piece be connected to others?

-   Does the piece provide empirical evidence and if so, is it compelling? If not, why?

-   What would I do if I worked on the same subject?

-   What would be the practical implication(s)--or policy propositions--based on this piece?

-   Recommended readings are by definition required. They are not the subject of reading summaries. Including them in the reading summaries does not affect the grade.

```{r}
#| fig-cap: "."
#| filters:
#| - parse-latex

library(dplyr)
library(tinytable)
library(kableExtra)
library(flextable)

grades <- c("compelling & creative evaluation of readings (<i>you made me cry</i>)",
            "accurate summary of the readings in <b>your own words</b> (<i>I don't see any problem here</i>)",
            "all required readings are discussed with reasonable clarity",
            
            "meeting minimal requirements"
)

col1 <- c("$\\checkmark$", "$\\checkmark$", "$\\checkmark$", "$\\checkmark$")
col2 <- c("", "$\\checkmark$", "$\\checkmark$", "$\\checkmark$")
col3 <- c("", "", "$\\checkmark$", "$\\checkmark$")
col4 <- c("", "", "", "$\\checkmark$")
          
df <- data.frame(grades = grades, 
                 `5.0-4.5` = col1,
                 `4.4-4.0` = col2,
                 `3.9-3.5` = col3,
                 `3.4-3.0` = col4,
                 check.names = F)

kbl(df,
    escape = F,
    full_width = F,
    align = 'lcccc')  %>%
  column_spec(1, width="7cm") %>%
  kable_paper()




```

-   Students are expected to hand in **four**, and only four, summaries of readings.
    -   Starting from the week of 'Institutions' and up to the near-end of the semester (see the schedule below for the specific date), you can choose whichever week's readings you want to work on. (this overlap with the week of your case presentation)
    -   The goal is to that you understood and thought about the major points of the readings (though not every single detail). Repeating the jargon used in the abstract (or 'light paraphrasing') would work against you. Show you did the reading. Use your own words.
    -   The length should not exceed 800 words. There's no minimum but a summary would typically be somewhere between 500 and 800 words.
    -   You might want to touch upon of the questions mentioned above.
    -   While there's no specific template for this assignment, a good summary would, you know, summarize all of the required readings of the week. It would also discuss 1) what the reasoning behind the authors' arguments is and 2) how (some of) the readings can be related to each other (e.g., A disagrees with B; C complements D; E expands F for XYZ reasons) in a {compelling} way. Again, delivering this with your own words, not jargon, is the key.
        -   Each summary accounts for 5% of your class grade.
        -   The summary is due **7:00 pm**, the class day (right before the class, that is).
-   There is no textbook you need to purchase. Instead, the reading list for each week is specified below. But if you want to have a reasonable textbook-like foundation for what we discuss, which is pretty advanced, this should be helpful (again, not a requirement):
    -   Oatley, Thomas. 2018. *International Political Economy*. 6th ed. New York, NY: Routledge.
-   Most of the readings are electronically available via GMU library webpage (as well as in Google Scholar [{{< fa brands google-scholar >}}](scholar.google.com)).
    -   This is part of the training; I will be more than happy to help if necessary.
    -   The readings you cannot access electronically will be made available in Canvas ('Files' section).
    -   Did you know you can actually link your Mason account to Google Scholar? This way, you don't have to navigate the Mason Library webpage to find the readings available to you. You can just use Google Scholar (which is much easier) to do that. See this simple instruction in [this link](https://library.gmu.edu/tutorials/linkingtogooglescholar).
-   I have a bad habit of replacing the existing readings with newer ones in the middle of a semester. But I assure you that such a change will happen no later than one week before when the reading (summary) is due. It would be, thus, a good idea to simply bookmark this syllabus page and check whether you have the up-to-date version of the reading list.

## Participation (20%) {#sec-part}

-   Active participation in class discussions is expected of every student in this graduate seminar. As is the case in any seminar, we learn the most when we talk. Answering my questions during the lecture and making an in-class comment on the class subject (or making an online comment on your classmates' presentation) are typical--but effective--ways of 'participation.'
-   Another way of participation is to partake in current event discussions. Every class will begin with discussions on a couple of current events related to global political economy. You might want to bring up a news article and we can discuss that. This is optional and designed to add to your participation grade. Note that as a Mason student, you have free access to the Financial Times, the New York Times, the Economist, and many others. Check out this [link.](https://infoguides.gmu.edu/news) for further information.
-   The evaluation of your participation rests upon my **subjective** assessment of the extent to which you contributed to our collective understanding of the class subject. In practical terms, both frequency and quality matter. In general, though, questions and comments on the <red>readings</red> are considered of a much better quality than others. There's no 'right' way of participation, but roughly speaking:

```{r}
library(dplyr)
library(gt)

col1 <- c("frequency", "quality")
col2 <- c("high", "high")
col3 <- c("medium", "high")
col4 <- c("high", "medium")
col5 <- c("medium", "medium")
col6 <- c("very low", "ver low")

df <- data.frame(col1, col2, col3, col4, col5, col6)

df %>% 
  gt() %>%
  tab_spanner(
    label = "20.0-19.0",
    columns = c(col2),
  ) %>%
  tab_spanner(
    label = "18.9-15.0",
    columns = c(col3, col4)
  ) %>%
  tab_spanner(
    label = "14.9-12.0",
    columns = c(col5)
  ) %>%
  tab_spanner(
    label = "11.9-0.0",
    columns = c(col6)
  ) %>%
  cols_label(
    col1 = "",
    col2 = "",
    col3 = "",
    col4 = "",
    col5 = "",
    col6 = ""
  ) %>%
  tab_options(column_labels.hidden = F) %>%
  cols_width(
  col2 ~ px(180),  
  col3 ~ px(180),  
  col4 ~ px(180),   
  col5 ~ px(180),
  col6 ~ px(180)) %>%
  cols_align(
    align = "center", 
    columns = c(col2, col3, col4, col5, col6) 
  ) %>%
  tab_style(
    style = cell_text(style = "italic"),  #weight="bold"
    locations = cells_body(
      columns = col1,
      rows = c(1,2)) 
  )

```

## Case Report (20% $\times$ 2 = 40%) {#sec-report}

```{r}
#| fig-cap: "."
#| filters:
#| - parse-latex

library(dplyr)
library(tinytable)
library(kableExtra)
library(flextable)

grades <- c("extraordinarily insightful analysis of the case (<i>you made me cry</i>)",
            "in-depth analysis of a concrete topic (<i>I don't see any problem here</i>)",
            "proper format w/ reasonable clarity",
            
            "meeting minimal requirements"
)

col1 <- c("$\\checkmark$", "$\\checkmark$", "$\\checkmark$", "$\\checkmark$")
col2 <- c("", "$\\checkmark$", "$\\checkmark$", "$\\checkmark$")
col3 <- c("", "", "$\\checkmark$", "$\\checkmark$")
col4 <- c("", "", "", "$\\checkmark$")
          
df <- data.frame(grades = grades, 
                 `20.0-18.5` = col1,
                 `18.4-17.0` = col2,
                 `16.9-13.0` = col3,
                 `12.9-10.0` = col4,
                 check.names = F)

kbl(df,
    escape = F,
    full_width = F,
    align = 'lcccc')  %>%
  column_spec(1, width="7cm") %>%
  kable_paper()




```

### the logistics 

-   The deadline for each Report/presentation is <red>7:00 PM, Tuesday</red> (Canvas) in the week of the subject. By this time both the Report and presentation video should be submitted in the designated places in Canvas.
-   Each Report should not exceed 2,500 words. There is no minimum but it'll be difficult to keep it under 1,500 words.
-   You will give a brief (10 minutes max., but preferably around 6-7 minutes) presentation of your Report via a video posted in Canvas. You <red>have to</red> have presentation slides. Your face should be visible at least for some parts of the presentation although wearing a mask is allowed.
-   The evaluation will be based on both your presentation (2%) and paper (18%).
    -   Presentations are part of evaluation. While aesthetics of presentation slides do not matter, clarity (of the message) and effectiveness (of how the message is delivered) do. Don't excessively beautify your slides, but make them clear and effective. 
    -   The presentation grade includes your handling of your peers' reaction (e.g., answering questions posted in Canvas). So check back on your presentation to see if there are questions. 
-   For each case report, you will decide which country (or countries or organization) you are interested in. Pick two.
    -   For each case report, you will also decide which topic (i.e. which week's theme) you are interested in. Pick two.
        -   Make sure your topic actually speaks directly to the topic of the week. If your report is on immigration, for example, the migrants' hardship coming through the American southern border, though important, is not a good topic. 'Why migrants choose to move to the US' is.
        -   You are not required to work on the same country for both presentations/Reports, though that's encouraged. 

### the expectation

-   The more specific your subject and question-answering the report, the better. For instance, ‘Why did the cash transfer program in 2018 fail in a Tigray Regional government’ is infinitely better than ‘Poverty Trap in Ethiopia.’
  -   The former is a rigorous and scientific way to address the latter. That's something people actually want to know.
  -   The latter would be more or less a generic punditry essay that can be done without actually engaging any theoretical or empirical work. You can write it without any graduate school education. In effect, <red>large language models like ChatGPT can write it much better than most of us.</red> So you don't need to be trained on this at all--there's no human job for that.
  -   How do you know if you are doing the former, not the latter? See if you identify (and discuss in detail) an example emblematic of the problems of microfinancing programs in that Nigerian town. Try to offer specifics. A good question you can keep asking yourself while working on this is, 'Do I pose a 'why' question? Do I show any evidence of this? Is it compelling?'. This will take a significant amount of time and effort as you are doing {real research} here. But it's worth it.
    -   In other words, avoid generality. If your Report reads pretty much like, for example, 'hey, the biggest problem of the Belize economy is corruption and it is based on political, economic, social, and cultural factors, but you know what, it's really about neoliberalism and colonialism---so let me summarize 100 years of its history,' you're not doing it right. Not exactly like this, but if you find few, if any, specific examples of what you're talking about in your Report, you are coming close to this.
-   Again, examples. The more, the better.
-   If your topic sounds like a book project, you're not doing it right. It should sound a lot more like a chapter in a book. Even better, a section of a chapter of a book.
-   *One*, though not the only, safe way to make sure that you have narrowed down the scope of your case and identified something specific is to focus on a particular development program (or any other economic policy program) and evaluate it. You might try to answer questions like: There are of course infinite different ways to do this.
-   These are all just examples and there are of course many other ways to do your case report!
-   Your case report should be building on a *synthesis* (not a summary) of <red>four</red> or more academic sources ([what are academic sources?](https://www.youtube.com/watch?v=GBZTqSXYODo)). This includes not only the sources that offer empirical elements for your case report but also materials that help you with the theoretical framing of the report.
    -   For example, let's say you work on a cash-transfer program in Burkina Faso. You might not have a whole lot of helpful sources on the country (which is actually good news, by the way, because you're taking up a novel subject!!!). However, there are a good deal of great academic research on cash transfer programs in other countries. There are numerous cross-country studies on that too. Nobody can say these aren't relevant. Do build on those studies. Try to borrow their analytical framework.
-   If the empirical part of your report relies solely on one source specifically talking about the very subject you're working on, that's not great (though not completely prohibited). It's prone to biases and misled conclusions. Bad science, in other words.
-   If you found a paper/report that completely answers the question you had in mind, that should be really bad news because what you're doing is just redundant.
-   It might be nice if some of our class readings are discussed in your report, but this is not required.
-   As a tip for writing a research paper, [this](https://sitesmedia.s3.amazonaws.com/politicalsci/files/2012/08/Guidelines-on-Writing-Research-Papers.pdf) should be helpful. The 'literature review' might not be directly relevant to this course though.

## Final Exam (20%) {#sec-final}

-   the exam date is determined by [the University](https://registrar.gmu.edu/wp-content/uploads/Final-Exams-202570.pdf). You cannot take it early or later than the designated date except for a medical emergency.
-   This essay exam will broadly reflect one of the general themes of the seminar and answer questions about our readings. Discussing non-class readings won't be helpful (and potentially hurt your grade).
  -   It is designed in a way that if you regularly complete the readings throughout the semester, you need to put in little extra effort for it.
-   Write an essay and submit it to Canvas (Assignment section).
-   Two questions will be given through Canvas **36** hours in advance, which is 7:30 <mark2>AM</mark2>, 12/15. 
-   36 hours are given solely for flexibility. The actual exam-taking wouldn't take more than three hours. Many of you work and/or have other important commitments. So what you are asked is simply to carve out several hours from this 36-hour window. 
  - In other words, this is not a traditional 'take-home essay' that would take up an extensive amount of time to complete. It is a regular essay-type final exam that is allowed to be taken at any time during this 36-hour window at a place convenient to you.
-   Be familiar with the University [policy](https://academicaffairs.chss.gmu.edu/ugradpolicies/ugpolicies/final-exams) on final exams.
-   More details will be provided when we get closer to the end of the semester.



# COURSE POLICY {#sec-policy}

The guiding principles of this course are *fairness* and *transparency*.

## Attendance

-   Regular attendance is required. While the number of absences would not proportionally translate into course reductions, an absence would curtail the opportunity to participate in class discussions, thereby leading to low participation grades.
-   Missing more than 5 classes without my written approval will result in zero in the participation grade.
-   The following constitutes 'absence':
    -   not attending class without my written approval
    -   arriving significantly late for class
    -   an unconsulted early departure
    -   being out of class for a lengthy period time
-   Life happens and a lot of things can get in the way. You can use '<red>life-happened</red>.' This triggers a one-time extension for the assignment (whichever it is) as well as an excuse for an absence. No question asked. No justification needed. In fact, when you use this, please don't explain the circumstances to me. This does *not* apply to the final exam. Just drop me one email simply stating that:

> "I need to use 'life-happend' for this week X. I have X due, and the new deadline now is Y.

### Medical Excuses

-   You can call in sick and ask for an extension. You're advised to consult the disability office in case your absence is expected to be lengthy.
-   There will be no real-time Zoom-in to the class (the University policy). You will be responsible for completing the readings on your own although I can answer any questions you might have afterwards.

## Assignment Submission

-   All assignments are expected to be submitted electronically in Canvas ('Assignment' section). Do not email any assignments.
-   Technical difficulties are not rare. Try to submit it early if you can.
-   Be sure to make it a MS Word or PDF file. Absolutely NO Pages file. Just so you know, as Mason students you have free access to MS Office software. You can also 'export' a Page file into a Word file.
-   For all details (e.g., citation styles), strictly adhere to the GLOA MA Student Guide. If you repeatedly and consistently violate citation styles, some, though a small amount, points will be taken off.
    -   [Research](https://www.iza.org/publications/dp/14614/costly-mistakes-why-and-when-spelling-errors-in-resumes-jeopardise-interview-chances) has shown that people read a lot from basic mistakes in easy-to-correct things.

## Feedback on Written Assignments

You can expect to have written feedback on your within 10 days. Please make sure that you see the in-text comments/feedback as well as the 'comment' (explained in the video). All Case Reports with grades should include my feedback. If any of yours does not, please let me know. There will be no feedback on your unless explicitly requested.

## Accommodations

If you have a documented learning disability or other condition that may affect academic performance you should: 1) Make sure this documentation is on file with the Office of Disability Services (SUB I, Rm. 222; 993-2474; [www.gmu.edu/student/drc](www.gmu.edu/student/drc)) to determine the accommodations you need; and 2) Discuss with me to plan your accommodation needs. Accommodations cannot be provided unless the document from the ODS is provided in advance.

## Academic Integrity

George Mason is an Honor Code university; please see the official [University Document](https://oai.gmu.edu/wp-content/uploads/2018/08/George-Mason-University-Honor-Code-2018-2019-final.pdf) for a full description of the code and the honor committee process. Don't rely on Reddit or your friends. They don't know and are very often misleading.

Remember, not being familiar with the Honor Code doesn’t constitute a sufficient ground to get your offense excused—anybody taking Mason courses (even a student-to-be) is subject to the Honor Code. Likewise, note that intentionality rarely makes a proper excuse. The principle of academic integrity is taken very seriously and violations are treated gravely.

When you rely on someone else’s work, you will give that source full credit, typically in the form of an in-text citation and bibliographic reference. If you are unaware of what counts as plagiarism see here: <http://mason.gmu.edu/~montecin/plagiarism.htm>. Students caught violating the Honor Code will receive a failing grade in the related course assignment and will be reported to the proper university authorities for further disciplinary action.

Academic integrity is also more than not commiting plagiarism. Lying, for example, is also an offense identified in the Honor Code. Let's build our class on the foundation of mutual respect and transparency.

## Use of Artificial Intelligence

A Large Language Model (LLM), commonly referred to as AI, is a double-edged sword, in that it can help you research better but doing so could easily involve plagiarism/cheating. As a general rule, making an LLM ‘write,’ be it partial or entirely, is considered unequivocal cheating (‘consulting unauthorized materials’) and a direct violation of GMU Honor Code.

Doing so also risks committing plagiarism. The writing itself has to be yours and yours only.Note that a ‘light’ rephrasing (e.g., altering some words) is still plagiarism. Similarly, submission of an edited version of LLM-generated writing is still considered plagiarism.

LLM could be used in the *process* of research, the result of which *you* actually write about. A good example is to use LLM in finding topics. The more you dig in, the more useful the outcome. One way to see if you are using LLM properly is to see how much time and energy you’re spending on it. If it takes a lot of effort and committing many hours of time to a task, you are probably using LLM right (as a general rule, if what it does is simply make your life more comfortable, there’s a good chance that you’re violating the Honor Code).

Another way is to use LLM to find relevant readings, although this is proven quite unreliable. A lot of 'new' AI models (which are actually based on a couple of existing AI engines) boast about how good they are at this, but so far they really haven't been.

You can also use AI to detect typos or *obvious/simple* grammar errors. However, if you let it offer basically the whole prose for you, then it's considered plagiarism. An easy way to tell this is to ask youself: "Could I come up with this kind of expression/sentence myself?" If the answer is 'no' or 'not sure,' then you have to stay away from it. Remember, this is not a writing or literature class and, however elegant, your prose is not relevant for your grades. Only clarity matters.

*Not bothering using an LLM in the first place remains a great option.*

## Diversity Statement

-   This section reflects in part Mason’s [diversity statement](https://stearnscenter.gmu.edu/purpose-and-mission/mason-diversity-statement/).

George Mason University promotes a living and learning environment for outstanding growth and productivity among its students, faculty, and staff. Through its curriculum, programs, policies, procedures, services, and resources, Mason strives to maintain a quality environment for work, study and personal growth.

An emphasis upon diversity and inclusion throughout the campus community is essential to achieve these goals. Diversity is broadly defined to include such characteristics as, but not limited to, race, ethnicity, gender, religion, age, disability, and sexual orientation. Diversity also entails different viewpoints, philosophies, and perspectives. Attention to these aspects of diversity will help promote a culture of inclusion and belonging, and an environment where diverse opinions, backgrounds and practices have the opportunity to be voiced, heard and respected.

There’s a practical element here too. You (will) live in an increasingly diverse society where practicing inclusiveness might help you in the long run (even if you do not agree with some of these values!). It is the obligation of the student to provide faculty, within the first two weeks of the semester, with the dates of major religious holidays on which they will be absent due to religious observances.

## Grading Scale

```{r, echo=F, message=F}

source2 <- data.frame(
    Point.Total = c(
      "93.00 or higher",  
      "90.00 - 92.99",   
      "87.00 - 89.99",    
      "83.00 - 86.99",  
      "80.00 - 82.99",  
      "70.00 - 79.99",  
      "69.99 or lower"
    ),
  Letter.Grade = c("A or A+", "A-", "B+", "B", "B-",  "C", "F")
)

library(tinytable)
tt(source2)
```

The grading scale in this course follows [GMU Catalogue](https://catalog.gmu.edu/policies/academic/grading/#ap-3-2).

-   The class does not give ‘I’ (incomplete) unless you have already completed about 95% of the course requirement.
-   Please note that there is no ‘round up’ of scores at the end of the semester. 92.99999, for example, is A–.
-   CHSS strictly prohibits giving an extra assignment for the purpose of improving a grade. I adhere to this policy.

# READING SCHEDULE

  - Readings are mostly available online. If not, they can be found in Canvas ('Files' section) even if it doesn't say so.
  -   Unless familiar with quantitative social science methodologies, you will find some of the readings too 'math-heavy.' It is *not* the purpose of this class for you to have a line-by-line understanding of the quantitative parts of each reading. You are asked, instead, to figure out what the authors actually want to deliver through all those numbers and equations. We will work on this whenever necessary and I am more than happy to help you on this individually.
  -   Unless specified as <mark>not required</mark>, all the listed readings are required readings. 'Not required' readings are not the subject of reading summaries. They are the kind of readings that we wouldn't have enough time to cover (but are still pretty helpful if you're interested in the subject).
  -   Readings and the reading schedules are subject to change. In fact, to reflect most up-to-date events in economic and political globalization, it is not uncommon that new readings are inserted and some readings are dropped. Although I try my best to give you at least one week before such changes, it is advisable that you do not complete the reading too much in advance.
  - If links to newspapers (NYT, FT, WSJ, or The Economist) do not work, use your own search. As Mason students, you have free access to these outlets.

## Week 1. Aug 26. First Day {.unnumbered}

  -  Class intro. There are readings, but no reading summary yet.
  -  Set the presentation schedule.
  -  King, G., Keohane, R. O., and Verba, S. (1994). *Designing Social Inquiry: Scientific Inference in Qualitative Research*. Princeton University Press, Princeton. Ch. 1.
  - Grossmann, M. (2021). *How Social Science Got Better: Overcoming Bias with More Evidence, Diversity, and Self-Reflection*. Oxford University Press. Chs. 1 and 6 are required and other chapters are optional. (This book is available online through GMU Library)
  -  Gerring, J. (2012). *Social Science Methodology: A Unified Framework*. Cambridge University Press, Cambridge, second edition. Chs. 1 and 2. <mark>not required</mark>
  -  Miller, S. (2014). Reading a Regression Table: A Guide for Students. [link.](https://svmiller.com/blog/2014/08/reading-a-regression-table-a-guide-for-students/)
    : <font size=2>You can actually understand most of the readings without reading these ‘regression tables’ and we won’t spend time on this matter unless there’s a specific question. But knowing this opens up much more intellectual opportunities. So give it a careful read.</font>

## Week 2. Sep 2. What are Development and Economic Globalization? {.unnumbered}

  -  No reading summary yet.
  -  Rapley, J. (2007). *Understanding Development: Theory and Practice in the Third World*. Lynne Rienner, Boulder. Ch. 1 & 2. 
  -  World Bank. (2024). World Development Report 2024. [link.](https://www.worldbank.org/en/publication/wdr2024). Chs. 2 and 8 only.
  -  Martinez, L. R. (2022). How Much Should We Trust the Dictator’s GDP Growth Estimates? *Journal of Political Economy*, 130(10):2731–2769.
  -  Steger, M. (2005). *Globalism: Market Ideology Meets Terrorism*. Rowman & Littlefield, New York, NY. Ch. 4.
  -  Acemoglu, D. (2010). Theory, general equilibrium, and political economy in developing economics. *Journal of Economic Literature*, 24:17–32. <mark>not required</mark>
  -  Solow, R. M. (1956). A contribution to the theory of economic growth. *Quarterly Journal of Economics*, 70(1):65–94. <mark>not required</mark>
  -  The Economist. (2019). “The Middle Income Spread” [link.](https://www.economist.com/graphic-detail/2017/10/11/the-middle-income-spread??fsrc=scn/fb/te/bl/ed/themiddleincomespread&fbclid=IwAR3LKWm8Qk2gaNF-I7kB90fUxFu6-b0_ZWW_TC-EzhDnWxNX6ovqMYECAdc) <mark>not required</mark>

## Week 3. Sep 9. Institutions and development {.unnumbered}

  -  first week where you can do a reading summary.
  -  North, D. C. (1991). Institutions. *Journal of Economic Perspectives*, 5(1):97–112.
  -  Sokoloff, K. L. and Engerman, S. L. (2000). History Lessons: Institutions, Factor Endowments, and Paths of Development in the New World. *Journal of Economic Perspectives*, 14:217–232.
  -  Acemoglu, D., Johnson, S., and Robinson, J. (2001). The colonial origins of comparative development: An empirical investigation. *American Economic Review*, 91:1369–1401.
  -  Acemoglu, D., Johnson, S., and Robinson, J. (2005). The Rise of Europe: Atlantic Trade, Institutional Change, and Economic Growth. *American Economic Review*, 95:556–579.
  - Ricart-Huguet, J. (2022). The Origins of Colonial Investments in Former British and French Africa. *British Journal of Political Science*, 52(2), 736–767.
  -  Olson, M. (1993). Dictatorship, democracy, and development. *American Political Science Review*, 87:567–576.
  -  Michalopoulos, S. and Papaioannou, E. (2016). The long-run effects of the scramble for Africa. *American Economic Review*, 106(7):1802–48. <mark>not required</mark2>
  -  Besley, T., Burgess, R., Khan, A., and Xu, G. (2022). Bureaucracy and development. *Annual Review of Economics*, 14(1):397–424. <mark>not required</mark>
  -  Jales, H., Kang, T. H., Stein, G., and Garcia Ribeiro, F. (2018). Measuring the role of the 1959 revolution on Cuba’s economic performance. *The World Economy*, 41(8):2243–2274. <mark>not required</mark>

## Week 4. Sep 16. (Modern) Trade and Development {.unnumbered}

  -  first week where you can do a presentation.
  - Caliendo, L. and Parro, F. (2022). Lessons from US-China Trade Relations. *Annual Review of Economics*, 15:513–541.
  -  Owen, E. and Johnston, N. P. (2017). Occupation and the political economy of trade: Job routineness, offshorability, and protectionist sentiment. *International Organization*, 71(4):665– 699.
  -  Kim, I. and Osgood, I. (2019). Firms in Trade and Trade Politics. *Annual Review of Political Science*. 2019. 22:399–417
  -  Carter, D. B. and Poast, P. (2020). Barriers to trade: How border walls affect trade relations. *International Organization*, 74(4):165–185.
  - Brutger, R., & Guisinger, A. (2024). Framing Layoffs: Media Coverage, Blame Attribution, and Trade-Related Policy Responses. *Political Behavior*, Forthcoming. DOI: [https://doi.org/10.1007/s11109-024-09960-8]( https://doi.org/10.1007/s11109-024-09960-8). 
  -  Chang, H.-J. (2003). *Kicking Away the Ladder: Development Strategy in Historical Perspective*. Anthem Press, London. Ch. 4. <mark>not required</mark>
  -  Guasti, A. and Koenig-Archibugi, M. (2022). Has global trade competition really led to a race to the bottom in labor standards? *International Studies Quarterly*, 66(4):sqac061.
  -  Autor, D. H., Dorn, D., and Hanson, G. H. (2016). The China Shock: Learning from LaborMarket Adjustment to Large Changes in Trade. *Annual Review of Economics*, 8:205–240. <mark>not required</mark>
  -  Handley, K. and Limão, N. (2022). Trade policy uncertainty. *Annual Review of Economics*, 14(1):363–395. <mark>not required</mark>
  -  Autor, D. H., Dorn, D., and Hanson, G. H. (2015). Why Obama’s key trade deal with Asia would actually be good for American workers. *Washington Post*. 3. 12. 2015. <mark>not required</mark>. PDF in Canvas.
  -  Blanchard, E. J., Brown, C. P., and Shor, D. (2019). Did Trump’s Trade War Impact the 2018 Election. NBER Working Paper 26434. [link.](http://www.nber.org/papers/w26434) <mark>not required</mark>
  -  Eichengreen, B. (2018). Trade policy and the macroeconomy. *IMF Economic Review*, Forthcoming. DOI: [https://doi.org/10.1057/s41308-018-0053-9.](https://doi.org/10.1057/s41308-018-0053-9) <mark>not required</mark>

## Week 5. Sep 23.  Finance and Development {.unnumbered}

Those who like to present on this week might note that the primary focus is on debt, banking, currency, and exchange rates. 

  -  Schneider, C. J. and Tobin, J. L. (2020). The Political Economy of Bilateral Bailouts. *International Organization*, 74(1):1–29.
  -  Ballard-Rosa, C., Mosley, L., and Wellhausen, R. L. (2021). Coming to Terms: The Politics of Sovereign Bond Denomination. *International Organization*, Forthcoming. Doi: [https://doi.org/10.1017/S0020818321000357](https://doi.org/10.1017/S0020818321000357)
  -  Tertytchnaya, K., De Vries, C. E., Solaz, H., and Doyle, D. (2018). When the money stops: fluctuations in financial remittances and incumbent approval in Central Eastern Europe, the Caucasus and Central Asia. *American Political Science Review*, 112(4):758–774.
  -  Broz, J. L. and Werfel, S. H. (2014). Exchange rates and industry demands for trade protection. *International Organization*, 68(2):393–416.
  -  Steinberg, D. A. and Shih, V. C. (2012). Interest Group Influence in Authoritarian States: The Political Determinants of Chinese Exchange Rate Policy. *Comparative Political Studies*, 45(11):1405–1434.
  -  Prasad, E. S. (2014).*The Dollar Trap*. Princeton University Press, Princeton, NJ. Part 4. Canvas.
  - Guisinger, A. (2023). “Good to Know: The Federal Reserve and U.S. monetary policy” [link.](https://goodauthority.org/news/explainer-federal-reserve-and-us-monetary-policy/?fbclid=IwAR0UQxvS58nk_jbs3PZi8Ddn75KLTeIRe0s7W-6XBQjuFn2KroawcI0YUiY)
      - This is a required reading, but do *not* include it in the reading summary (if you’re doing one this week). It’s a ‘soft explainer.’
  -  Frieden, J. (2008). Globalization and exchange rate policy. In Zedillo, E., editor, *The Future of Globalization*, pages 344–357. Routledge, New York. [link.](http://scholar.harvard.edu/files/jfrieden/files/globalization_and_exchange_rate_policy.pdf) <mark>not required</mark>
  -  Eichengreen, B. and Leblang, D. (2008). Democracy and globalization. *Economics & Politics*, 20(3):289–334. <mark>not required</mark>.
  -  Rodrik, D. and Subramanian, A. (2009). Why does financial globalization disappoint? *IMF Staff Papers*, 56(1):112–138 <mark>not required</mark>.
  -  Ferguson, N. (2018). *The Ascent of Money*. New York: Penguin. <mark>not required</mark>
  -  Reichert-Facilides, D. (2023) New York rewrites the rules on sovereign debt restructurings. Financial Times. June 2, 2023. [https://www.ft.com/content/213aa90a-3eba-445](https://www.ft.com/content/213aa90a-3eba-4451-a509-b9d17e1d56c8) <mark>not required</mark>
  - Reuters. (2025) The 'Triple A' soeverign bond club has shrunk. Reuters. May 19, 2025. [link](https://www.reuters.com/business/finance/triple-a-sovereign-bond-club-has-shrunk-2025-05-19/?utm_campaign=trueAnthem%3A+Trending+Content&utm_medium=trueAnthem&utm_source=facebook&fbclid=IwY2xjawKYQEdleHRuA2FlbQIxMQBicmlkETE4WWpreXl4bExINGNQSFNMAR6oXF0qeDFo0Y3qqUgOw8UUqMVM5hgakl7VaVQ60O8D9_cKx-kNFWx8CDtUZA_aem_-z_hfkLGYPha5G0PyxScow). <mark>not required</mark>
  - Smith, I., Herbert, E., and Abboud, L. (2025). France joins Eurozone's 'periphery' as turmoil deepens, say investors. Financial Times. September 9, 2025. [link](https://on.ft.com/3JYbuUi)

## Week 6. Sep 30. Investment and Development {.unnumbered}

Presenters might note that the focus is essentially foreign direct investment (FDI) from the perspectives of host governments, originating governments, investors, and/or people involved. Some of the easiest ways to approach this topic would be to start with particular multinational corporations as they are usually the investors.

  -  Frieden, J. A. (1994). International investment and colonial control: A new interpretation. *International Organization*, 48:559–593.
  -  Büth, T. and Milner, H. V. (2014). Foreign direct investment and institutional diversity in trade agreements: Credibility, commitment, and economic flows in the developing world, 1971–2007. *World Politics*, 66(1):88–122.
  -  Blanton, S. L. and Blanton, R. G. (2007). What Attracts Foreign Investors? An Examination of Human Rights and Foreign Direct Investment. *Journal of Politics*, 69(1):143–155.
  -  Malesky, E. J. and Mosley, L. (2018). Chains of love? global production and the firm-level diffusion of labor standards. *American Journal of Political Science*, Forthcoming.
  -  Christensen, D. (2019). Concession Stands: How Mining Investments Incite Protest in Africa. *International Organization*, 73(1):65–101.
  -  Yang, Y. (2023). Racing to the bottom?: Chinese foreign direct investment and collective labor rights. *International Interactions*, Forthcoming. DOI: [https://doi.org/10.1080/ 03050629.2023.2260934.](https://doi.org/10.1080/03050629.2023.2260934)
  - Blair, G., Christensen, D., & Wirtschafter, V. (2022). How Does Armed Conflict Shape Investment? Evidence from the Mining Sector. *Journal of Politics*, 84(1), 116–133. 
  -  Chilton, A. S., Milner, H. V., and Tingley, D. (2018). Reciprocity and public opposition to foreign direct investment. *British Journal of Political Science*, Forthcoming. <mark>not required</mark> 
  - Blattman, C. and Dercon, S. (2017). Everything we knew about sweatshops was wrong. New York Times. April 27. 2017. [link.](https://www.nytimes.com/2017/04/27/opinion/do-sweatshops-lift-workers-out-of-poverty.html) <mark>not required</mark>
  -  Giles, C., Abboud, L., and Agyemang, E. (2021). Global tax deal backers battle to win over holdout countries. Financial Times. June 29, 2021. [link.](https://www.ft.com/content/562fa83d-1af2-4002-82b8-fded22d2df51)<mark>not required</mark>
  -  Moon, C. (2015). Foreign direct investment, commitment institutions, and time horizon: How some autocrats do better than others. *International Studies Quarterly*, 59(2):344–356. <mark>not required</mark>
  -  Bechtel, M. M. (2009). The political sources of systematic investment risk. *Journal of Politics*, 71:661–677. <mark>not required</mark>
  - Jensen, N. (2008). Political risk, domestic institutions, and foreign direct investment. *Journal of Politics*, 70(4):1040–1052. <mark>not required</mark>.

## Week 7. Oct 7. International Economic Organizations and Development {.unnumbered}

  - *We read a bunch of very short articles in this week. For more textbook-like discussions, refer to* Copelovitch *and* Stiglitz *below*.
  -  Daoud, A., Nosrati, E., Reinsberg, B., Kentikelenis, A. E., Stubbs, T. H., and King, L. P. (2017). Impact of International Monetary Fund programs on child health. *Proceedings of the National Academy of Sciences*, 114(25):6492–6497.
  -  Nooruddin, I. and Woo, B. (2015). Heeding the Sirens: The Politics of IMF Program Participation. *Political Science Research and Methods*, 3(1):73–93.
  -  Stone, R. W. (2004). Political Economy of IMF Lending in Africa. *American Political Science Review*, 98(3):577–592.
  -  Humphrey, C. (2017). He who pays the piper calls the tune: Credit rating agencies and multilateral development banks. *The Review of International Organizations*, 12(2):281–306.
  -  Busch, M. L. and Pelc, K. J. (2019). Words matter: How WTO rulings handle controversy. *International Studies Quarterly*, 63(3):464–476.
  -  Editorial Board (2021). The United States can help the IMF to rethink how it lends. *Nature*, 592:325–326.
  -  The Economist (2002). The Fund Bites Back, July 4. [https://www-economist-com. mutex.gmu.edu/finance-and-economics/2002/07/04/the-fund-bites-back ](https://www-economist-com.mutex.gmu.edu/finance-and-economics/2002/07/04/the-fund-bites-back)(Alternatively, use the GMU [library page](https://infoguides.gmu.edu/isec/news) of the Economist Online and type in the title in quotes in the search).
  -  Davis, C. L. and Morse, J. C. (2018). Protecting trade by legalizing political disputes: Why countries bring cases to the International Court of Justice. *International Studies Quarterly*, 62(4):709–722. <mark>not required</mark>
  -  Vreeland, J. R. (2002). The Effect of IMF Programs on Labor. *World Development*, 30:121– 139. <mark>not required</mark>
  -  Stiglitz, J. (2002). *Globalization and Its Discontents*. Norton & Company, New York, NY. <mark>not required</mark>
  -  Copelovitch, M. S. (2010). *The International Monetary Fund in the Global Economy*. Cambridge University Press, New York, NY. <mark>not required</mark>
  -  Abouharb, M. R. and Cingranelli, D. L. (2006). The Human Rights Effects of World Bank Structural Adjustment, 1981–2000. *International Studies Quarterly*, 50(2):233–262. <mark>not required</mark>
  -  Arauz, A. and Cashman, K. (2022). Special drawing rights one year later, by the numbers. CEPR Working Paper. Available at: [https://cepr.net/special-drawing-rightsone-year-later-by-the-numbers/.](https://cepr.net/special-drawing-rights-one-year-later-by-the-numbers/) <mark>not required</mark>

## Week 8. Oct 14. Foreign Aid {.unnumbered}

Those interested in presenting in this week should be aware that foreign aid is very diverse and any presentation would need to explain what kind of aid it is talking about. For example, 'DRC's aid dependency' would be quite a tough topic to pull off because it points to a very wide array of things. 'What happened to the food assistance to Nicaragua in 1998?' would be more doable. In addition, humanitarian aid, usually a very important topic, would be hard to work on because its connection to economic globalization and/or development is very hard to explain.

  -  Williams, M. (2018). The political economy of unfinished development projects: Corruption, clientelism, or collective choice? *American Political Science Review*, 111(4):705–723.
  - Findley, M. G., Harris, A. S., Milner, H. V., and Nielson, D. L. (2017). Who Controls Foreign Aid? Elite versus Public Perceptions of Donor Influence in Aid-Dependent Uganda. *International Organization*, 71(4):633–663.
  -  Kosack, S. and Tobin, J. (2006). Funding Self-Sustaining Development: The Role of Aid, FDI, and Government in Economic Success. *International Organization*, 60(2):205–243.
  -  Sexton, R. and Zürcher, C. (2023). Aid, Attitudes, and Insurgency: Evidence from Development Projects in Northern Afghanistan. *American Journal of Political Science*, Forthcoming. DOI: [https://onlinelibrary.wiley.com/doi/pdf/10.1111/ajps.12778.](https://onlinelibrary.wiley.com/doi/pdf/10.1111/ajps.12778)
  -  Baker, A. (2015). Race, Paternalism, and Foreign Aid: Evidence from U.S. Public Opinion. *American Political Science Review*, 109(1):93–109.
  -  Andersen, J. J., Johannesen, N., and Rijkers, B. (2020). Elite Capture of Foreign Aid: Evidence from Offshore Bank Accounts. Policy Research Working Paper 9150. World Bank Group. Available at: [https://www.nielsjohannesen.net/wp-content/uploads/AJR2020 -WBWP.pdf.](https://www.nielsjohannesen.net/wp-content/uploads/AJR2020-WBWP.pdf) <mark>not required</mark>
  -  Easterly, W. (2007). *The White Man’s Burden*. Penguin, New York, NY. <mark>not required</mark> Non-academic Book
  -  Addison, T. and Baliamoune-Lutz, M. (2017). Aid, the Real Exchange Rate and Why Policy Matters: The Cases of Morocco and Tunisia. *Journal of Development Studies*, 53(7):1104– 1121. <mark>not required</mark>
  -  Djankov, Simeon, J. M. and Reynal-Querol, M. (2008). The curse of aid. *Journal of Economic Growth*, 13(1):169–194. <mark>not required</mark>
  -  Alesina, A. and Dollar, D. (2000). Who gives foreign aid to whom and why? *Journal of Economic Growth*, 5(1):33–57. <mark>not required</mark>
  -  Edwards, S. (2015). Economic development and the effectiveness of foreign aid: A historical perspective. *Kyklos*, 68(3):277–316. <mark>not required</mark>. An accessible primer of foreign aid history.

## Week 9. Oct 21. Poverty & Inequality Reduction {.unnumbered}

Those presenting this week might want to know that there's a difference between poverty/inequality and general under-development. A developed country might still have poverty issues, for example.


  -  Briggs, R. (2018). “Millions of Americans as destitute as the world’s poorest? Don’t believe it.” Vox. February 4, 2018. [https://www.vox.com/the-big-idea/2018/2/1/169596 34/millions-americans-destitute-2-day-worlds-poorest-deaton-aid.](https://www.vox.com/the-big-idea/2018/2/1/16959634/millions-americans-destitute-2-day-worlds-poorest-deaton-aid) 
  -  Rudra, N. and Tirone, D. C. (2017). Trade, Politics, and the Poor: Is Sen Right and Bhagwati Wrong? *Studies in Comparative International Development*, 52(1):1–22.
  -  Attanasio, O., Augsburg, B., De Haas, R., Fitzsimons, E., and Harmgart, H. (2015). The impacts of microfinance: Evidence from joint-liability lending in Mongolia. *American Economic Journal: Applied Economics*, 7(1):90–122.
  -  Banerjee, A., Duflo, E., Glennerster, R., and Kinnan, C. (2015a). The miracle of microfinance? evidence from a randomized evaluation. *American Economic Journal: Applied Economics*, 7(1):22–53.
  -  Banerjee, A., Duflo, E., Goldberg, N., Karlan, D., Osei, R., Parienté, W., Shapiro, J., Thuysbaert, B., and Udry, C. (2015b). A multifaceted program causes lasting progress for the very poor: Evidence from six countries. *Science*, 348(6236).
  -  Premand, P. and Rohner, D. (2023). Cash and Conflict: Large-Scale Experimental Evidence from Niger. *American Economic Review: Insights*, 6(1), 137–153. DOI: [https://doi.org/10.1257/aeri.20230069](https://doi.org/10.1257/aeri.20230069).
  - Linardi, S. and Rudra, N. (2020). Globalization and willingness to support the poor in developing countries: An experiment in India. *Comparative Political Studies*, 53(10-11):1656– 1689.<mark>not required</mark>
  -  Hendrix, C. S. and Haggard, S. (2015). Global food prices, regime type, and urban unrest in the developing world. *Journal of Peace Research*, 52(2):143–157. <mark>not required</mark>
  -  Milanovic, B. (2020). “The World is Becoming More Equal," *Foreign Affairs*. [link.](https://www.foreignaffairs.com/articles/world/2020-08-28/world-economic-inequality) <mark>not required</mark>
  -  Dollar, D. (2005). “Globalization, Poverty, and Inequality since 1980,” *World Bank Research Observer* 20: 145-185. <mark>not required</mark>
  -  Basu, K. (2006). Globalization, poverty, and inequality: What is the relationship? what can be done? *World Development*, 34:1361–1373. <mark>not required</mark>


## Week 10. Oct 28. Political Economy of Immigration {.unnumbered}

Those presenting this week are advised to **not** to focus on non-political economy dimension of the topic, such as 'the cruelty of the immigration policies of country X' or 'the agony of migrants.' It is important, but no directly related to our course subject. 

  -  Leblang, D. and Peters, M. E. (2022). Immigration and globalizagtion (and deglobalization). *Annual Review of Political Science*, 25:377–399.
  -  Fitzgerald, J., Leblang, D., and Teets, J. C. (2014). Defying the law of gravity: The political economy of international migration. *World Politics*, 66(3):406–445.
  -  Alrababa’h, A., Dillon, A., Williamson, S., Hainmueller, J., Hangartner, D., and Weinstein, J. (2021). Attitudes toward migrants in a highly impacted economy: Evidence from the Syrian refugee crisis in Jordan. *Comparative Political Studies*, 54(1):33–76.
  -  Hangartner, D., Dinas, E., Marbach, M., Matakos, K., and Xefteris, D. (2019). Does exposure to the refugee crisis make natives more hostile? *American Political Science Review*, 113(2):442–455.
  -  Hainmueller, J. and Hopkins, D. J. (2015). The hidden american immigration consensus: A conjoint analysis of attitudes toward immigrants. *American Journal of Political Science*, 59(3):529–548.
  -  Bansak, K., Ferwerda, J., Hainmueller, J., Dillon, A., Hangartner, D., Lawrence, D., and Weinstein, J. (2018). Improving refugee integration through data-driven algorithmic assignment. *Science*, 359(6373):325–329.
  - Alkousaa, R. (2025). A German Town Hoped Migration Could Turn Its Fortunes around. It Was No Panacea. Reuters. [link](https://www.reuters.com/world/europe/german-town-hoped-migration-could-turn-its-fortunes-around-it-was-no-panacea-2025-08-31/) (September 2, 2025). PDF availabe in Canvas.
  -  Just, A. (2015). The far-right, immigrants, and the prospects of democracy satisfaction in europe. *Party Politics*, page doi:10.1177/1354068815604823. <mark>not required</mark>
  -  Mosley, L. and Singer, D. A. (2015). Migration, labor, and the international political economy. *Annual Review of Political Science*, 18(1):283–301. <mark>not required</mark>
  -  Hainmueller, J. and Hangartner, D. (2013). Who gets a swiss passport? a natural experiment in immigrant discrimination. *American Political Science Review*, 107(1):159–187. <mark>not required</mark>

## Week 11. Nov 4. No Class (Election Day)

## Week 12. Nov 11. Global Economic Crisis {.unnumbered}
Those presenting this week should note that we are talking about actual crises, not general economic difficulties. You should be able to point to a crisis as an event.


  -  <mark2>Last</mark2> week where you can do a presentation.
  -  Kindleberger, C. P. (1978). *Manias, Panics, and Crashes: A History of Financial Crises*. John Wiley & Sons, Inc., New York Chs. 1 and 2. Canvas
  -  The Economist (2014). Don’t Lie to Me, Argentina. The Economist. June 20th 2014. Available at: [https://www.economist.com/leaders/2014/06/20/dont-lie-to-me-ar gentin~a~.](https://www.economist.com/leaders/2014/06/20/dont-lie-to-me-argentina) Also in Canvas
  - Oatley, T. (2019). Toward a political economy of complex interdependence. *European Journal of International Relations*, 25(4):957–978.
  -  Campello, D. (2014). The Politics of Financial Booms and Crises: Evidence from Latin America. *Comparative Political Studies*, 47:260–286.
  -  Quaglia, L. and Verdun, A. (2023). Explaining the     response of the ecb to the covid-19 related economic crisis: inter-crisis and intra-crisis learning. *Journal of European Public Policy*, 30(4):635–654.
  -  Bloomberg. 2023. “What Happened to SVB? Your Silicon Valley Bank Qs,” Bloomberg Businessweek. March 16, 2023. [link.](https://www.bloomberg.com/news/features/2023-03-16/what-happened-to-svb-your-silicon-valley-bank-qs-answered?utm_source=website&utm_medium=share&utm_campaign=copy) <mark>not required</mark>
  -  Remmer, K. L. (1990). Democracy and economic crisis: The Latin American experience. *World Politics*, 42(3):315–335. <mark>not required</mark>
  -  The Guardian. (2021). ‘As bad as Brexit’: Turkey faces currency crisis after Erdoğan sacks bank chief. March 21, 2021. [link.](https://www.theguardian.com/world/2021/mar/21/turkish-lira-could-plunge-15-as-erdogan-faces-market-wrath-for-sacking-bank-chief?CMP=share_btn_url) <mark>not required</mark>
  -  Dönmez, P. E. and Zemandl, E. J. (2019). Crisis of capitalism and (de-) politicisation of monetary policymaking: reflections from hungary and turkey. *New Political Economy*, 24(1):125– 143. <mark>not required</mark>
  -  Reinhart, C. and Reinhart, V. (2020). The pandemic depression: The global economy will never be the same. Foreign Affairs. August 6, 2020. Available at: [link.](https://www.foreignaffairs.com/articles/united-states/2020-08-06/coronavirus-depression-global-economy) <mark>not required</mark>


## Week 13. Nov 18. Global Health, Environment & Resource {.unnumbered}

  -  Last week where you can do a reading summary.
  -  Savoia, A. and Sen, K. (2021). The political economy of the resource curse: A development perspective. *Annual Review of Resource Economics*, 13:203–223.
  -  Fails, M. D. (2020). Oil income and the personalization of autocratic politics. *Political Science Research and Methods*, 8(4):772–779.
  -  Son, B. and Bellinger, N. (2022). The Health Cost of Autocratization. *Journal of Development Studies*, 58(5):873–890.
  -  The Economist (2019). Germany’s pricey “coal exit”. The Economist. Sep 19th 2019. Available at: [https://www.economist.com/europe/2019/09/21/germanys-pricey-co al-exit.](https://www.economist.com/europe/2019/09/21/germanys-pricey-coal-exit)
  -  Kallis, G., Kostakis, V., Lange, S., Muraca, B., Paulson, S., and Schmelzer, M. (2018). Research on degrowth. *Annual Review of Environment and Resources*, 43:291–316.
  -  Terzi, A. (2024). Degrowth is a dead end. Project Syndicate. March 6, 2024. [link.](https://www.project-syndicate.org/commentary/degrowth-movement-is-politically-impractical-by-alessio-terzi-2024-03)<mark>not required</mark>
  -  Andrew McAfee. 2020. Why Degrowth Is the Worst Idea on the Planet. Wired Oct 6, 2020. [link.](https://www.wired.com/story/opinion-why-degrowth-is-the-worst-idea-on-the-planet/) <mark>not required</mark>
  - Bayer, P. and Urpelainen, J. (2016). It is all about political incentives: democracy and the renewable feed-in tariff. *The Journal of Politics*, 78(2):603–619. <mark>not required</mark>
  -  Lawrence, R. Z. (2024). Climate action: Implications for factor market reallocation. PIIE Working Paper. 24-1. [link.](https://www.piie.com/sites/default/files/2024-01/wp24-1.pdf) <mark>not required</mark>

## Week 14. Nov 25. Economic Security and De-globalization {.unnumbered}

  -  *The readings in this week are particularly prone to change, so stay tuned*.
  -  Poast, P. (2022). The ‘Golden Age’ of Globalization is Officially Over. World Politics Review. October 21, 2022. [link.](https://www.worldpoliticsreview.com/china-us-trade-war-globalized-economy/)
  -  Danzman, S. B. (2022). CHIPS+ could change the U.S. semiconductor supply chain, and more, Washington Post. August 9, 2022. [link.](https://www.washingtonpost.com/politics/2022/08/09/chips-act-semiconductors-supply/?utm_medium=social&utm_source=twitter&utm_campaign=wp_monkeycage)
  - Hayashi, Y. 2023. WSJ News Exclusive | U.S. to Allow South Korean, Taiwan Chip Makers to Keep Operations in China. Wall Street Journal. [Link.](https://www.wsj.com/articles/u-s-to-allow-south-korean-taiwan-chip-makers-to-keep-operations-in-china-5d7d72cc).
  -  Swanson, A. and Wong, E. (2022). With New Crackdown, Biden Wages Global Campaign on Chinese Technology. New York Times. October 13, 2022. [link](https://www.nytimes.com/2022/10/13/us/politics/biden-china-technology-semiconductors.html)
  -  Kumar, A. and Lipsky, J. (2022). The dollar has some would-be rivals. meet the challengers. New Atlanticist. September 22, 2022. Atlantic Council. [link.](https://www.atlanticcouncil.org/blogs/new-atlanticist/the-dollar-has-some-would-be-rivals-meet-the-challengers/)
  -  Dempsey, H. and Hook, L. China set to tighten grip over global cobalt supply as price hits 32-month low. Financial Times. March 12. 2023. Available at: [link](https://www.ft.com/content/abf28c9f-54e2-45c2-8dac-c5016bd31423?fbclid=IwAR0IART6s2ckhWDIR7jmr1ZvDWO22i9W8U1nUPi5KGx0OKfujujs5QvbvSY)
  -  Agarwal, R. (2023). Industrial policy and growth strategy trilemma. Finance & Development. International Monetary Fund. Available at: [link.](https://www.imf.org/en/Publications/fandd/issues/Series/Analytical-Series/industrial-policy-and-the-growth-strategy-trilemma-ruchir-agarwal?utm_medium=email&utm_source=govdelivery)
  -  Eichengreen, B. (2022). Sanctions, swift, and china’s cross-border inter-bank payments system. CSIS Briefs. May 20, 2022. [link.](https://www.csis.org/analysis/sanctions-swift-and-chinas-cross-border-interbank-payments-system)

## Week 15. Dec 2. Wrap-up & Course Evaluation {.unnumbered}

## Final Exam {.unnumbered}

  - 12/8 is the last day of the semester for the [University.](https://registrar.gmu.edu/wp-content/uploads/Final-Exams-202570.pdf)
  - <red>**12/16**</red>: Final Essay Due, 7:30 PM 
  -  The final exam schedule is determined entirely by the University authority. It is thus subject to the University’s schedule change.
  -  Essay questions made available 36 hours in advance (7:30 <mark2>AM</mark2>, 12/15); no exceptions
  -  Submission via Canvas (by 7:30 PM). So we do *not* meet.
  - Detailed instructions will be provided as we approach the end of the semester.
