---
title: "GLOA 400-02 GLOA Capstone"
subtitle: Fall 2026. TR 1:30--2:45 PM <br> Innovation Hall 323 [📍](https://maps.app.goo.gl/4QEBDLp3j4YNuVLB9)
title-block-banner: "green"
title-block-banner-color: "yellow"
format: 
  html:
#    math: mathjax
    number-sections: true
    theme: cosmo
    table-markdown: true
#    self-contained: true
#editor: visual
# author:
#   - name: "Byunghwan 'Ben' Son (bson3@gmu.edu)"
#     meta-data:
#       custom-info: "Office Hours"
#     affiliations:
#       - name: Global Affairs, George Mason University
#         url: https://globalaffairs.gmu.edu/


#csl: C:\\Users\\kalka\\Dropbox\\latex\\apsa.csl
toc: true
toccolor: blue
smooth-scroll: true

execute:
  warning: false
  message: false
  error: false
  echo: false
#bibliography: references.bib
---

```{=html}
<style>


mark {
  background-color: #ece985;
  color: black;
  border-radius: 5px; 
  padding: 0.2em;
}

mark2 {
  background-color: #840a73;
  color: white;
  border-radius: 5px; 
  padding: 0.2em;
}

red {
  color: #9b1212;
}

blue {
  color: #124921;
}

</style>
```

**Change log** <font size=1>(Bookmark this webpage. Any changes made will be specified here.)</font> 

- <font size=2>Aug 14: A subsection on IRB is added (@sec-irb).</font>
- <font size=2>Aug 14: A not-required reading is added to Oct 1 </font>

# Instructor

-   Byunghwan 'Ben' Son (bson3\@gmu.edu)
    -   Associate Professor of Global Affairs
    -   [{{< fa house size=small >}} Personal Webpage](https://textvulture.github.io/)
    -   [{{< fa school-flag size=small >}} GLOA Profile](https://globalaffairs.gmu.edu/)
    -   [{{< fa brands github >}} Github](https://github.com/textvulture)
    -   [{{< fa brands google-scholar >}} Google Scholar](https://scholar.google.com/citations?user=h0o27GgAAAAJ&hl=en)
-   Office Hours
    -   TR 10:15--11:45 AM. 6235 [Horizon Hall](https://maps.app.goo.gl/4QEBDLp3j4YNuVLB9)
    -   Zoom-in during this time is also available, but you have to let me know at least two hours in advance. Emails are strongly preferred to Zoom.
    -   I will make myself available for a bit before and after the class. Take advantage of that time.
-   Email Communications
    -   You can email me whenever you want, but my responses to the emails sent to me after 5 pm weekdays as well as any time during the weekend will be significantly slow. For best responses, you might want to try to use the normal working hours (9 AM to 5 PM, Monday through Friday).
    -   In your email, please indicate <red>who you are</red> and <red>which class you're in (i.e., GLOA 400)</red>.
    -   For security reasons, emails not sent from the Mason account (i.e., gmu.edu) won't be answered. Not only is it Mason's rule, it is also (and perhaps more importantly) a smart thing to do. Even when looking 'innocent,' emails from a non-Mason account won't be answered. If you are not getting my response to your email for a long time, first check if you sent it from your Mason account.

# Course Description

The primary goal of this class is to get help you complete an independent research project (see @sec-synthesis and @sec-impact) that has direct relevance to globalization. You will go through the entire process of completing a social science research project. In doing so, you will wrap up and revisit your course taking experience in GMU as a Global Affairs major, which is what a capstone course is really about. This will be probably the most demanding, but also possibly most rewarding, course that you take in GMU. You are responsible from the beginning to the end of your project, which will require your attention constantly. Unlike others, the class includes significant amount of one-on-one meetings as well as self-guided writing times. By presenting your own work and giving feedback to others', the course also offers a great opportunity to train yourself for professional communication skills. 


## Learning Outcomes

1.  **Understand knowledge creation**: Students will understand how global knowledge is generated and communicated, and how it can be used to address questions or problems in disciplines and in society.
2.  **Engage multiple perspectives**: Students will be able to identify and negotiate multiple perspectives on globalization, work collaboratively within and across multiple contexts, and engage ethically with their subject and with others.
3.  **Investigate a meaningful question**: Students will use scientific inquiry skills to articulate a question; engage in an inquiry process; and situate the concepts, practices, or results within a broader context.
    -   <font size='2'>Students will be able to ask increasingly complex questions about significant global problems, debates, or challenges.</font>
    -   <font size='2'>Students will be able to evaluate and choose research methods that are appropriate to a project.</font>
    -   <font size='2'>Students will be able to explain how a project has value to professional, scholarly, or global contexts.</font>
4. **Scholarly Communication**: Students will be able to present the findings of their research project in an effective and communicative way and provide constructive feedback when presented with research of others.

## Mason Core Synthesis {#sec-synthesis}

The course fulfills the Mason Core 'Synthesis' requirement. Upon completing this course, students are expected to be able to (required of any Mason Core synthesis course):

1.  Communicate effectively in both oral and written forms, applying appropriate rhetorical standards (e.g., audience adaptation, language, argument, organization, evidence, etc.)
2.  Using perspectives from two or more disciplines, connect issues in a given field to wider intellectual, community or societal concerns
3.  Apply critical thinking skills to evaluate the quality, credibility and limitations of an argument or a solution using appropriate evidence or resources

## Mason IMPACT+ {#sec-impact}

GLOA 400 (any section) is also a [Mason IMPACT+](https://impact.gmu.edu/) course in the area of Research, Scholarly, and Creative Activities. *What this actually means* to us is that students taking this class have to **a)** complete a research project, collaborative or individual (which has always been the case for a capstone course, anyway) and **b)** present the project outside of the classroom.

This presentation is <red>not graded</red> as long as you complete one (note, though, that there is a separate in-class presentation that *is* graded). For the out-of-classroom presentation, you can choose *one* or more from the options below. My recommendation is that everybody participates in the GLOA research week and those who wish to may also pursue one of the other two options, additionally. Note that this can be done after the semester. Also note that the title of your project can be listed in your transcript just like the honors' which is a great opportunity.

-   *GLOA Research Week*
    -   At the end of the semester. The exact date will be announced later but it usually is the first week of the last month of the semester (May or December). Both online and in-person are available. This is your <red>default option</red> and no extra steps (i.e., application) are required if this is taken. Presenting here in and by itself fulfills the IMPACT+ requirement. There usually is a cash reward for a select group of presenters.
-   *CHSS Undergraduate Research Symposium*
    -   This takes place late in the semester as well (a couple of weeks before the finals, usually). A project done in a Fall class can be presented, which counts toward the IMPACT+ requirement. <red>You have to apply for it.</red>
-   *OSCAR URSP*
    -   Mason OSCAR's [Undergraduate Research Scholars Program](https://oscar.gmu.edu/) (URSP) is a semester-long program where students pursue their research project funded by the University under the guidance of a faculty mentor (in this case, me). This is probably the most competitive (and therefore rewarding) option. You have to apply in advance and need to be selected to continue on the process. Presenting the research at the 'celebration of the student scholarship' at the end of the semester counts toward the IMPACT+ requirement.

**Opportunities from the Mason IMPACT+ [Office](https://provost.gmu.edu/academics/undergraduate-education/mason-impact/research-scholarly-and-creative-activities)**

-   Students can receive a line on their transcripts for their specific project by uploading their projects via the portal on the student section of the Mason Impact website.
-   Students can receive a MINI Grant for up to $500 to complete their project. Applications will be considered on a rolling basis until a set deadline (check the office [webpage](https://provost.gmu.edu/academics/undergraduate-education/mason-impact/micro-and-mini-grants)).
-   Students can continue their work as part of the Undergraduate Research Scholars Program.
-   Students can share their project at the Celebration of Student Scholarship and Impact.



# COURSE REQUIREMENT

In a nutshell, your grade is determined by:

- Idea Pitch (5%) @sec-pitch
- Literature Review (5%) @sec-lit
- Presentation #1 (5%) @sec-pres1
- Presentation #2 (15%) @sec-pres2
- Peer Review (20%) @sec-peer
- Research Paper (30%) @sec-paper
- Participation (20%) @sec-part

## The topic

There's no grade specifically assigned to what kind of topic you choose. But picking up the right topic is tremendously important and will affect the grades of other items significantly. Topics should be related to globalization, broadly defined. Consider the following when choosing your topic. You are encouraged to discuss your topic with me in advance.

-   **Public**: Not your or someone else's personal experience but an event (or the news thereof) that a sizeable number of the global public was exposed to. A 'controversy' that happened only at a corner of the internet might not qualify. If the topic was covered quite a bit by the global media, that's a safe bet.
-   **The premise is based on verifiable facts**: A story of an individual based on rumors wouldn't cut it. Try to avoid the cases built on mere accusations. As a general rule, empirically unverifiable subjects cannot be studied scientifically.
-   **At least some components of the story cross a border**: Something that 1) happened solely within a country and 2) matters only to that country would not qualify. Granted, few of such one-country events exist these days. An otherwise purely domestic topic that has important and clear implications beyond the border (e.g., election; secessionist movement; populism; mass displacement; economic crisis) will also qualify.

Your project will be much more in-depth, focused, and analytical than, say, a Wikipedia entry. Limiting the time frame and/or geographical coverage would be a good strategy. A descriptive overview that reads like a 'social commentary' or a punditry essay should be avoided. A generic chronicling of an event is also undesirable. Be concrete, specific, and focused. This will take time and effort. And your capstone is that much more valuable.

Another way to think about the concreteness of the topic is to see if your presentation can focus on a specific event/example that represents the topic. In other words,

| Not Cool {{< fa face-frown size=small >}} | Better {{< fa face-smile size=small >}} |
|-------------------------------------|-----------------------------------|
| Territorial disputes in the South China Sea | Younger Filipinos' reactions to the new security post in the Spratly Islands |
| Rohingya refugee crisis | Comparing the narratives of different political factions in Myanmar on the Rohingya genocide |
| China's Covid-19 policies | How did the containment of Shanghai happen in 2022? The case of the Apple factory |
| US and China trade war | The effect of the US tariffs on Chinese steel imports in 2021--3 |
| North Korean nuclear crisis | How/whether the May 2022 NK missile launch was different from previous ones |
| Supply chain disruptions and US-China decoupling | The effect of the CHIPS Act on the semiconductor production of TSMC |

: <font size='2'>You might have already noticed it--you will have to work on the things in the left column to actually do the research focusing on the topics in the right column.</font>



## Idea Pitch (5%) {#sec-pitch}

Early in the semester, you will share your rough ideas on the potential topic of your capstone project. It's a five-minute pitch, unstructured. Do *not* bring in slides. Just verbally deliver 1) what the topic you are thinking about for your project is; 2) why you think that's interesting; 3) how you'll go about it. 

The class will be divided into Units A and B (announced a week before). When one unit gives a pitch (individually), the other has to provide verbal feedback and suggestions, focusing on how doable the proposed idea sounds. In the end, you will have provided feedback for <red>**at least two pitches**</red>. At this stage, any feedback should be highly valuable. As far as you offer one pitch, the grade will reflect mostly your feedback. The more concrete and constructive, the better.


## Literature Review (5%) {#sec-lit}

- Complete the research paper <red>up to</red> the literature review.
- For a generic instruction on how to write a research paper, see [this YouTube video](https://youtu.be/3uy5ZGYAQQ4?si=iDSF3KibkiB86xtc). Not all of this is strictly applicable to what we do (refer instead to the lecture video for details of what literature review is about), but it should give you a rough idea of how to do it.
- You are expected to turn in a mostly-finished Literature Review of your paper as well as rudimentary **Introduction**. What this means is that you also have a reasonably clear 'argument' to offer.
- In the literature review:
  - include at least six academic sources (narrowly defined, such as academic books or peer-reviewed journal articles). You are also encouraged to use non-academic sources as much as you want including policy reports, blog posts, news or magazine articles, but they don’t count towards the 6 academic sources requirement.
  - highlight the contribution of your paper to the literature. This doesn’t have to be (or probably should not be) something grandiose. In fact, it has very little to do with ‘doing good things for the world.’ Boring stuff like ‘few people talked about X in country Y’s context’ is just fine. The important part here is to demonstrate ‘few people.’
  - include proper citations and references.
  - make sure to discuss theoretical stuff. By ‘theoretical,’ I mean general relationship between factors closely related to your project regardless of the empirical context---we will talk about this in more detail in class.
    - If, for example, your topic is a cash transfer programs in Sudan, a theoretical piece you might need to discuss is a general discussions on the effectiveness of cash transfer programs, foreign aid, or micro-credit programs in a much broader and not Sudan-specific context. This way, you can situate your project in the literature and easily identify what the possible contribution can be.

## Presentations {#sec-pres}

- The two presentations are not only important as a core step in the process of a research project, but also as a training ground where you can improve your professional communication skills. In almost all professions, these days, you will be expected to give presentations on your work, particularly when you are promoted in the organization. So why not work on that?

- The presentation is expected to be clear and succinct (such that we can have enough Q and A). Slides are required. There's no additional points for fancy slides. All that matters is clarity. Slides with too many or too few words wouldn't be effective. Submit your side in the designated place in Canvas before the beginning of your presentation (so practically, before class). DO NOT SEND ME YOUR SLIDES. 

- In evaluating the presentation, I will focus on:
    -   is the topic properly selected (see the 'public, verifiable, and cross-borderly' requirements above)?
    -   is the argument (or the main point) clearly presented and convincing?
    -   is the empirical evidence compelling? 
    -   is the overall delivery of the presentation effective, *not* circling around irrelevant background information?

### Presentation #1 (5%) {#sec-pres1}

The first presentation still contains all the elements of your project completed so far, but with the understanding that some of them can be incomplete. Keep your presentation to *7* minutes or shorter.

### Presentation #2 (15%) {#sec-pres2}

The second presentation assumes that your project now has all the pieces it needs, although they might need improvements. If there's any significant change from the first presentation, acknowledge it. Keep your presentation to *10* minutes or shorter.

## Peer Review (5% $\times$ 2 $\times$ 2 = 20%) {#sec-peer}
While everyone can provide feedback to any presentation, there will be **two** designated peer-reviewers for each of the presenters (announced a week in advance). This applies to both Presentations #1 and #2. In other words, you're providing written peer review reports for two presenters in Presentation #1 and two in Presentation #2. For each, you will fill out a form (found in Canvas) and submit it. The deadline for this form (completed) is 36 hours from the presentation. To clarify, this form-based peer review is not part of participation grade. They have their own grades. So if you are concerned about participation grade (@sec-part), you want to give ample in-class, verbal feedback too.


## Research Paper (30%) {#sec-paper}

- <mark2>**Due Noon, Dec 7**</mark2>
- The steps taken up to this point should naturally lead to a research paper, which is the final product of the class.
- As always, a proper citation style (e.g., APA) is required. No footnote citations (it's lame!). Instead, follow '(author-year)' citation.
- There's no particular reference style required, but use a generally accepted one (e.g., Chicago, APA, Harvard) consistently.
- The paper should not be longer than <red>5,000 words</red> inclusive of the references. It should be longer than 3000 words.
- The literature review that was turned in previously (@sec-lit) should be part of the paper, though it is expected to be *improved* upon it reflecting the feedback given.
- The basic format, as we discuss multiple times in class, should be:
  - Introduction
  - Literature Review
  - Argument/Theory/Hypothesis
  - Empirics (Data and Analysis)
  - Conclusion
- You have numerous templates for this. Most of the article-form readings you have had in this class--and other!--are great examples of research papers. Because you've regularly completed readings in these courses that you took, you are expected to be very familiar with what a research paper looks like.


### Rubric (or lack thereof)

There is no hard rubric for the written assignments. There are just so many different ways to do a good work. But here are some expectations for a certain level of grades. Concreteness is always an important factor that would explain the variation within each column in the table below.

```{r}
#| fig-cap: "."
#| filters:
#| - parse-latex

library(dplyr)
library(tinytable)
library(kableExtra)
library(flextable)

grades <- c("extraordinarily insightful analysis (<i>you made me cry</i>)",
            "direct answer with relevant points (<i>there's no major shortcoming</i>)",
            "proper format w/ reasonable clarity (<i>you are trying to make a point and I am confident that I understand it</i>)",
            
            "meeting all the minimal requirements (<i>it talks about a relevant topic and is submitted on time</i>)"
)

col1 <- c("$\\checkmark$", "$\\checkmark$", "$\\checkmark$", "$\\checkmark$")
col2 <- c("", "$\\checkmark$", "$\\checkmark$", "$\\checkmark$")
col3 <- c("", "", "$\\checkmark$", "$\\checkmark$")
col4 <- c("", "", "", "$\\checkmark$")
          
df <- data.frame(grades = grades, 
                 `30.0-29.0` = col1,
                 `28.9-26.0` = col2,
                 `25.9-22.0` = col3,
                 `21.9-15.0` = col4,
                 check.names = F)

kbl(df,
    escape = F,
    full_width = F,
    align = 'lcccc')  %>%
  column_spec(1, width="7cm") %>%
  kable_paper()

```

## Participation (20%) {#sec-part}

-   Regular attendance is the bare minimum requirement in this class.
-   Active participation in class discussion is expected of every student. As is the case in any class, we learn the most when we talk. In particular, participating in class discussions will help you navigate your own research topics and refine the research design you come up with. Try to approach other people's project in the context of 'what would I have done with that?'
-   The evaluation of your participation rests upon my **subjective** assessment of the extent to which you contributed to our collective understanding of the class subject. In practical terms, both frequency and quality matter. There are numerous ways to offer high-quality comments. However, making points about the <red>readings</red> or comments relating class discussions to your (or your classmates') project is considered always of the highest quality. In general though, the more, the better.
-   Engaging in your classmates' presentations (i.e., asking questions and offering feedback) is a great way of participation. To be clear, your *own* presentation is not participation (nor is the official written peer review done through the forms), meaning that you need to engage others' presentations if you want your speaking to count.
-   "**What's happening in the World?**": Another great way to participate is to contribute to a brief (3-min) class discussion taking place at the beginning of every meeting. Just bring up what you found from news on global affairs (broadly defined, but *not* US-specific news) and we can discuss it together. Note that as a Mason student, you have free access to the Financial Times, the New York Times, the Economist, and many others. Check out [this link](https://infoguides.gmu.edu/news) for further information.
-   The number of absences does not directly translate into the participation grades. However, a sustained absence (barring a medical excuse recognized by Disability Services) will have an impact. <red>five</red> or more absences by the end of the semester will lead to zero in the participation grade. Also note that absence indirectly affects your grade (since the less you're in class, that much fewer opportunities for your participation).


# COURSE POLICY {#sec-policy}

## Medical Excuses

-   You can call in sick and ask for an extension. You're advised to consult the disability office in case your absence is expected to be lengthy.
-   There will be no real-time Zoom-in to the class (the University policy). You will be responsible for completing the readings on your own although I can answer any questions you might have afterwards.

## Assignment Submission

-   All written assignments are expected to be submitted electronically in Canvas ('Assignment Submission' tab). Do not email any assignments.
-   Technical difficulties are not rare. Try to submit it early if you can.
-   Be sure to make it an MS Word or PDF file. This is the safest form that very rarely crashes. Just so you know, as Mason students you have free access to MS Office software. No Page files, please.
-   <red>2%</red> reduction in grade will be applied to a same-day late submission (so it is still a good idea to turn things in no later than the day of the deadline---the damage would be minimal!). An additional 5% reduction will be added for every midnight (11:59 pm) until the submission.

## Accommodations

If you have a documented learning disability or other conditions that may affect academic performance you should: 1) Make sure this documentation is on file with the Office of Disability Services (SUB I, Rm. 222; 993-2474; [www.gmu.edu/student/drc](www.gmu.edu/student/drc)) to determine the accommodations you need. Accommodations cannot be provided without this process.

## Use of Artificial Intelligence

A Large Language Model (LLM), commonly referred to as AI, is a double-edged sword, in that it can help you research better but doing so could easily involve plagiarism/cheating. As a general rule, making an LLM 'write,' be it partial or entirely, is considered unequivocal cheating ('consulting unauthorized materials') and a direct violation of [GMU Academic Standard](https://academicstandards.gmu.edu/), which applies to you even if you're unaware of it. Doing so also risks committing plagiarism because your using something that does not belong to you without a citation. The writing itself has to be yours and yours only. Note that a 'light' rephrasing (e.g., altering some words) is still plagiarism. Similarly, submission of an edited version of LLM-generated writing is still considered plagiarism. That means if you ask an LLM to generate a rough draft and then submit something that you revised heavily it still counts as a violation of the Academic Standard. 

LLMs could be used to employed in the *process* of research. A good example is to use an LLM in finding topics. For example, you want to work on foreign aid coming in the form of providing portable water (i.e., constructing wells), which you read an article about, but do not really know where to start. Ask LLMs to give you a list of successful and unsuccessful cases of such projects. Then you can start searching for the existing research on those specific cases.

This won't be a simple, over-night task. There's going to be hours spent in refining prompts and coming back to the drawing board many times. The more you dig in, the more useful the outcome. One way to see if you are using LLM properly is to see how much time and energy you're spending on it. My own use of LLM in my research is to run an iterative code that gives prompts to an LLM (using tokens) to determine the ideological leanings of millions of news headlines. I would have needed a lot of research fund to pull this through. 

If it takes a lot of effort and committing many hours, you are probably using LLM right. It gets you farther than you might have without it. If what it does is simply make your life more comfortable or save you from the deadline, I'd say there's a very good chance that you're violating the Honor Code). More importantly, by doing so, *you pay quite a bit of money for a valuable research/training opportunity and then just decline it while throwing away your conscience* (and potentially throwing yourself under the bus if caught).

<mark2>Not bothering using an LLM in the first place remains a great option.</mark2>

## Mutual Respect & Collegiality

You go to college to expose yourself to people who disagree with you. Exchanges of intellectual ideas in a safe and free environment are integral to our learning. However, this should not come at the expense of civility, which is a value of a higher order. No speech or action intended to result in—or in fact resulting in—mental or physical attacks on others (e.g., a statement denying the existence or human dignity of a group of people; a speech promoting violence) will be tolerated in this classroom. You are free to hold such views, but that freedom does not override others' right to feel safe in this class.

## Institutional Review Board {#sec-irb}

If your research involves non-human subjects such as historical sources, public data, news articles, you can just ignore this part. If you use public information, this subsection doesn't concern you either even if it's about humans (e.g., social media posts; online comments), although it is generally recommended that you anonymize the human sources in these cases. 

If you are to use a research or data collection method involving a human subject (e.g., human-facing experiment, interview, focus group, or participatory observation), you need to go through Institutional Review Board (IRB) [review](https://oria.gmu.edu/topics/human-subjects/irb-review-process/) with the university. A project that is strictly contained within a classroom, IRB could be waived. However, GLOA 400 is an IMPACT+ course, which requires the findings of all research projects to be shared outside the classroom. By definition, therefore, you will need an IRB review if your research involves a human subject. 

IRB takes time, sometimes stretching through months (thorugh rarely). If you're planning on human subject research and IRB is necessary, it is strongly recommended that you file the review within the first three weeks of the semester. The system requires you to submit many different materials at the time of application, so you need to have a pretty good understanding of how you go about your project by then.

## Grading Scale

```{r, echo=F, message=F}

source2 <- data.frame(
    Point.Total = c(
      "93.00 or higher",  
      "90.00 - 92.99",   
      "87.00 - 89.99",    
      "83.00 - 86.99",  
      "80.00 - 82.99",  
      "77.00 - 79.99",
      "73.00 - 76.99",
      "70.00 - 72.99",
      "60.00 - 69.99",
      "59.99 or lower"
    ),
  Letter.Grade = c("A", "A-", "B+", "B", "B-", "C+", "C", "C-", "D", "F")
)

library(tinytable)
tt(source2)
```

The grading scale in this course follows the [GMU Catalogue](https://catalog.gmu.edu/policies/academic/grading/#ap-3-2).

-   The class does not give 'I' (incomplete).
-   Please note that there is no 'round up' of scores at the end of the semester. 92.99999, for example, is A--.
-   In line with GMU policies, the class does not offer students any extra activities to grant extra grades/points towards the end of the semester to 'bump up' the grade. CHSS strictly prohibits giving an extra assignment for the purpose of improving a grade. I adhere to this policy.

### You 'earn' grades.

A word on what a grade means in this class, because it's different from what you're used to, say, in a stat or econ course. There, a problem set has a correct answer, and your grade is what's left after points are deducted for departures from it. Here there is no correct answer to depart from. A grade is not what remains after subtraction; it is what your paper <red>earns</red>. Two papers can both be free of identifiable problems and still receive different scores, because one of them did something the other didn't. So the question "I fixed everything you told me to fix---why isn't this a 100?" doesn't quite make sense. Addressing my comments addresses shortcomings, but it does not by itself produce a perfection. The top of the scale is reserved for insight. Note also what this means in the other direction: I can't hand you a checklist that guarantees full marks, and I won't pretend otherwise. What I *can* do is tell you where a draft is thin, what a sharper version of your question would look like, and which parts of your evidence aren't carrying the weight you think they are. I can help you get better than before. To be great, however, depends solely on the steps you make. 

## University Common Policies {#sec-common}

*The following is a summary of Mason's [Common Course Policies](https://stearnscenter.gmu.edu/home/gmu-common-course-policies/) (August 2026), which apply to every course at the University regardless of what any individual syllabus says. Read the full text at the link. Anything in @sec-policy above is in addition to—never instead of—these.*

### Academic Standards

Mason's academic standards rest on three principles:

- **Honesty**: give accurate information in all coursework, communications, and exams.
- **Acknowledgement**: credit every contribution to your work—ideas, words, and materials from others, cited in the style of the discipline—including shared authorship on group work.
- **Uniqueness of work**: submit only your own original effort. This covers writing, code, presentations, and exams, and it rules out self-plagiarism.

Plagiarism, fabrication, and cheating are among the violations handled under [University procedures](https://academicstandards.gmu.edu/), and sanctions can be academic, disciplinary, or both.

### Accommodations for Students with Disabilities

[Disability Services](https://ds.gmu.edu/) (SUB I, Suite 2500; 703-993-2474) coordinates reasonable accommodations. You can start the registration process at any point in your enrollment.

### FERPA and Course Communication

Course records are governed by [FERPA](https://registrar.gmu.edu/ferpa/). You <red>must</red> use your GMU email account for anything course-related; I cannot respond to—or send course content to—a non-Mason address.

### Title IX and Non-Discrimination

Mason's programs are to be free of discrimination on the basis of race, color, religion, ethnic or national origin (including shared ancestry), sex, disability, military or veteran status, sexual orientation, gender identity or expression, age, marital or pregnancy status, genetic information, or any other protected characteristic.

**Required reporting**: as a non-confidential employee, I am legally required to report to the [Office of Access, Compliance, and Community](https://oacc.gmu.edu/) (OACC), including the Title IX Coordinator, any details I learn—directly or indirectly—about discrimination or harassment. Reportable conduct includes Title VI/VII discrimination and harassment (unequal treatment, or conduct that is threatening, harmful, or humiliating) and Title IX Prohibited Conduct (sexual harassment, sexual assault, gender-based stalking, dating or domestic violence). OACC then assesses the report and may reach out to the person potentially harmed. Relevant policies: [1201](https://oacc.gmu.edu/access-services/non-discrimination), [1202](https://universitypolicy.gmu.edu/policies/sexual-harassment-policy/), [1204](https://universitypolicy.gmu.edu/policies/prohibited-relationships-with-students/). OACC: 703-993-8730, Aquia 373 (Fairfax) or Van Metre Hall Suite 222 (Mason Square).

**If you want a *confidential* conversation instead**, go to one of Mason's confidential offices: [SSAC](https://ssac.gmu.edu/), [CAPS](https://caps.gmu.edu/), [Student Health Services](https://shs.gmu.edu/), or the [Ombudsperson](https://ombuds.gmu.edu/).

# READING SCHEDULE {#sec-schedule}

-   Class discussions are built on the readings assigned here. Remember, though, the primary goal of this class concerns *your research* and all these readings and discussions about them are designed to help you pin down your topic of interest and help you refine the research design you constructed. Pay close attention to a) the way literature is evaluated, b) arguments/hypotheses are derived, c) data are described, d) research designs are explained, e) empirical evidence is presented, and f) conclusions are drawn.
-   Unless familiar with quantitative methods, you will find several of the readings 'math-heavy' (though they really aren't). It is *not* the purpose of this class for you to have a line-by-line understanding of the quantitative parts of each reading. You are asked, instead, to figure out what the authors actually want to deliver through all those numbers and equations. We will work on this whenever necessary and I am more than happy to help you on this individually. I am a quanitatively-oriented scholar, but I don't require students to use quanitative methods. In fact, without taking well-sequenced method courses, it is generally not a good idea to employ a quantitative research method for your capstone project.
-   Unless specified as <mark>not required</mark>, all the listed readings are required readings.
-   The readings can be--and will be--added or deleted. If it happens, it should happen at least one week before the reading is due. Just bookmark this syllabus page (because I will update it online) and check it before working on the readings.
-   Most readings here are available through the [GMU library webpage](https://library.gmu.edu/). It is part of the training that you get yourself familiar with finding these academic materials in the library (your tuition money goes to GMU's subscriptions to all these academic journals--many of which are quite a lot of {{< fa dollar-sign size=small >}}). Those unavailable in the Library or free online will be made available in Canvas ('Readings' in the 'Course Contents' tab).


## Aug 25. Introduction. Going over the Syllabus. {.unnumbered}

-   Introduction of the class: the class begins with the assumption that by August 25, you have read this syllabus quite thoroughly.
- **My Best Reading**: What was the single reading you liked the most in the classes that you've taken in GMU? Did it use data? What kind? There's no grade for this, but you will be asked to talk about it. 
- If you haven't already, start thinking about your capstone project topic right now.


## Sep 1. Idea Pitch I {.unnumbered}

- See @sec-pitch. Keep it to 5 minutes or less.
- Unit A of the class will pitch their ideas. Unit B will give feedback. 

## Sep 3. **NO CLASS** on Sep 3: Conference in Boston.  {.unnumbered}

## Sep 8. Idea Pitch II {.unnumbered}

- See @sec-pitch. Keep it to 5 minutes or less.
- Unit B of the class will pitch their ideas. Unit A will give feedback.

## Sep 10, 15. Social Science Methods Primer (1): the basics {.unnumbered}
<font size=2>For several class meetings, we will discuss social science research methods. Do not wait until the end of the method lectures (which will be too late) to choose your research method. Skim through the readings in advance and make an early selection. <red>Start working on it early in the semester</red>. The lecture and class discussion will serve as a reinforcement and/or refinement.</font>

- We will talk about: idea, variable, argument, theory, hypothesis, inference, test, and, most of all, science
- King, Gary, Robert O. Keohane, and Sidney Verba. 1994. *Designing Social Inquiry: Scientific Inference in Qualitative Research*. Princeton: Princeton University Press. **Chs. 1 and 2**. (This book is available online through GMU Library)
- Grossmann, M. (2021). *How Social Science Got Better: Overcoming Bias with More Evidence, Diversity, and Self-Reflection*. Oxford University Press. **Chs. 1 and 6** are required and other chapters are optional. (This book is available online through GMU Library)
-   Vennesson, Pascal. 2008. “Case Studies and Process Tracing: Theories and Practices.” In eds. Donatella della Porta and Michael Keating. *Approaches and Methodologies in the Social Sciences: A Pluralist Perspective*. New York: Cambridge University Press, 223–39. <mark>not required</mark>
-   Gerring, John. 2012. *Social Science Methodology: A Unified Framework*. 2nd Edition. Cambridge: Cambridge University Press. <mark>not required</mark>
-   Pape, Robert A. 2008. “[Methods and Findings in the Study of Suicide Terrorism](https://doi.org/10.1017/S0003055408080179).” *American Political Science Review* 102(2): 275–77. <mark>not required</mark>
-   APA Style Guide. <https://apastyle.apa.org/>. (for your reference--just take a look).
- By now, you're expected to have a pretty good idea of what you're topic is. Don't wait and start working on the resources, data, references, and literature. NOW.

## Sep 17, 22. How <red>Not</red> to Write a <blue>Bad</blue> Literature Review {.unnumbered}

-   <blue>You've completed a lot of readings in your coursework so far. Most of them have pretty good literature reviews (otherwise they wouldn't have survived peer-review processes). Therefore, by now, you must be able to tell what a good literature review looks like.</blue>
-   Knopf, Jeffrey W. 2006. “Doing a Literature Review.” *PS: Political Science & Politics* 39(1): 127–32.
-   Organizing Your Social Sciences Research Paper. University of Southern California Libraries. <https://libguides.usc.edu/writingguide/purpose>: use the tabs on the left.
-   The Literature Review: A Few Tips On Conducting It. University of Toronto. <https://advice.writing.utoronto.ca/types-of-writing/literature-review/>

## Sep 24, 29. Method Primer (2): Case Studies & Process Tracing {.unnumbered}

- Sep 29 (midnight) is the deadline for your literature review. See @sec-lit.
-   George, Alexander L., and Andrew Bennett. 2006. *Case Studies and Theory Development in the Social Sciences*. Cambridge: MIT Press. **Chs. 3 & 5 only**. PDF available in Canvas.
-   Steinberg, David A., and Victor C. Shih. 2012. “Interest Group Influence in Authoritarian States: The Political Determinants of Chinese Exchange Rate Policy.” *Comparative Political Studies* 45(11): 1405–34.
-   Ziblatt, Daniel. 2009. “Shaping Democratic Practice and the Causes of Electoral Fraud: The Case of Nineteenth-Century Germany.” *American Political Science Review* 103(1): 1–21.
-   Pepinsky, Thomas B. 2009. *Economic Crises and the Breakdown of Authoritarian Regimes: Indonesia and Malaysia in Comparative Perspective*. New York: Cambridge University Press. **Ch. 1 only.** Available online through GMU library.
- Andy Stapleton. 2022. "What makes a great research poster". YouTube video: [https://youtu.be/ZwiTqrVfDFU?si=zGUFDqJWupVj_2-8](https://youtu.be/ZwiTqrVfDFU?si=zGUFDqJWupVj_2-8).
- Fairfield, Tasha, and Andrew E Charman. 2022. **Social Inquiry and Bayesian Inference: Rethinking Qualitative Research**. New York, NY: Cambridge University Press.<mark>not required</mark>


## Oct 1, 6. Method Primer (3): (Qualitative) Content Analysis and Interview {.unnumbered}

-   Klašnja, Marko, Pablo Barberá, Nicholas Beauchamp, Jonathan Nagler, and Joshua A. Tucker. 2015. “Measuring Public Opinion with Social Media Data.” In *The Oxford Handbook of Polling and Polling Methods*. Oxford University Press, 555–82. <https://doi.org/10.1093/oxfordhb/9780190213299.013.3>. PDF available in Canvas.
-   Chiluwa, Innocent, and Presley Ifukor. 2015. “\`War against Our Children’: Stance and Evaluation In #BringBackOurGirls Campaign Discourse on Twitter and Facebook.” *Discourse & Society* 26(3): 267–96.
-   Bouvier, Gwen, and David Machin. 2018. “Critical Discourse Analysis and the Challenges and Opportunities of Social Media.” *Review of Communication* 18(3): 178–92.
-   Leech, Beth L. 2002. “Asking Questions: Techniques for Semistructured Interviews.” *PS: Political Science & Politics* 35(4): 665–68.
-   Fujii, Lee Ann. 2008. “The Power of Local Ties: Popular Participation in the Rwandan Genocide.” *Security Studies* 17(3): 568–97.
- Kim, Dae Young, and Byunghwan Son. 2025. “K-Pop Fan Perceptions and Negotiation of Alternative Forms of Masculinities.” *The Journal of Men’s Studies*: 10608265251394364. DOI: [https://doi.org/10.1177/10608265251394364](https://doi.org/10.1177/10608265251394364)
- Soest, Christian von. 2023. “Why Do We Speak to Experts? Reviving the Strength of the Expert Interview Method.” *Perspectives on Politics* 21(1): 277–87. <mark>not required</mark>


## Oct 8. Presentation #1 (1)  {.unnumbered}

## Oct 13. Presentation #1 (2)  {.unnumbered}


## One-on-One Meetings (Oct 15 through Nov 10) {.unnumbered}

- <blue>By now, the *first* draft (though very rough) of your Paper is expected to be close to completion. In the meetings you will show me what you have written (or tried to write) since the literature review.</blue>
- These meetings are integral (and unique) part of this course.
-   Sign-up sheets will be made available in advance.
-   The Zoom link will be made available in Canvas.
-   At least 30 minutes are guaranteed.
- You can have multiple meetings. *One is mandatory* (not having at least one-on-one meeting at all counts as two absences). It is recommended that you signed up for one early and another later. You probably don't want to sign up for one meeting only later in the schedule because that would leave you very little time to revise/update the paper.
-   Important: Use this time as your uninterrupted writing time. **<red>You will need it</red>**.

### Oct 15. One-on-One Meeting, Session #1 {.unnumbered}

### Oct 20. One-on-One Meeting, Session #2 {.unnumbered}

### Oct 22. One-on-One Meeting, Session #3 {.unnumbered}

### Oct 27.One-on-One Meeting, Session #4 {.unnumbered}

### Oct 29.One-on-One Meeting, Session #5 {.unnumbered}

### Nov 3. No Class. Election Day. {.unnumbered}

### Nov 5. One-on-One Meeting, Session #6 {.unnumbered}

### Nov 10. One-on-One Meeting, Session #7 {.unnumbered}

## Nov 12. Presentation #2 (1) {.unnumbered}

## Nov 17. Presentation #2 (2) {.unnumbered}

## Nov 19. Presentation #2 (3) {.unnumbered}


## Dec 1. Final one-on-one meeting (optional) {.unnumbered}

## Dec 3.  Course Wrap-up and Evaluation  {.unnumbered}

## Capstone Paper Due {.unnumbered}
- <mark2>Noon, Dec 7 (Monday)</mark2> 
- Submit a PDF or Word file to the designated place in Assignment section of Canvas.


# Online Data Resources {#sec-data}

Rarely do I see, while teaching this class, a quantitatively oriented research project. That's fine and understandable (because few people are asked to take a quantitative method class in GLOA). More often than not, though, people are just scared of using even a tiny bit of numerical data because of the inconvenience of learning statistical packages (or 'programs' such as R, Stata, or Matlab).

This is a shame because using some data could easily enrich the depth of your otherwise qualitative case study. Often it helps you contextualize the importance of your topic on a broader scope. Luckily, modern social science data sets tend to offer various online tools available. You don't need to learn any statistics (though that'd be awesome) to retrieve some data relevant to your topic. Even better, you can generate cool-looking graphs simply using some drop-down menus. I suggest that you at least play with these data sets.

-   [World Development Indicators (WDI)](https://data.worldbank.org/)
    -   any development-related indicators (not only economic and financial, but also social, public health, and gender-related variables) for almost all countries in the world over many years
-   [World Values Survey (WVS)](https://www.worldvaluessurvey.org/WVSOnline.jsp)
    -   individual-level survey data on various topics (social, cultural, political, and economic) covering multiple (but not very often) years for many countries
-   [Varieties of Democracy (V-Dem)](https://www.v-dem.net/graphing/graphing-tools/)
    -   political (particularly very detailed democracy-related ones) and social (e.g., corruption) data for almost all countries in the world for a very extensive period of time
